### 2020-09-02 manuscript/article.tex
initialize manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=communication]{achemso}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*\mycommand[1]{\texttt{\emph{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Ruben Goeminne}
\affiliation[TU Ghent]
{Center for Molecular Modeling
Ghent University
Tech Lane Ghent Science Park Campus A, 9052 Zwijnaarde, Belgium}

\author{Simon Krause}
\affiliation[University of Groningen]
{Stratingh Institute for Chemistry
Faculty of Mathematics and Natural Sciences
University of Groningen
Nijenborgh 4, 9747 AG Groningen, The Netherlands}

\author{Toon Verstraelen}
\affiliation[TU Ghent]
{Center for Molecular Modeling
Ghent University
Tech Lane Ghent Science Park Campus A, 9052 Zwijnaarde, Belgium}
\email{toon.verstraelen@ugent.be}

\author{Jack D. Evans}
\affiliation[TU Dresden]
{Department of inorganic chemistry
Technische Universität Dresden
Bergstraße 66, 01062 Dresden, Germany}
\email{jack.evans@tu-dresden.de}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
  {Mapping the complete thermodynamic landscape of gas adsorption for a responsive metal-organic framework}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{IR,NMR,UV}
\keywords{American Chemical Society, \LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  To do.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Advanced porous materials are poised for application.

It is often the flexibility of porous adsorbents that enables unparalleled performance in separation applications.

Responsive adsorbents, such as metal-organic frameworks, can significantly change pore structure and volume in response to stimuli.\cite{10.1021/acs.chemmater.5b00046}

One particularly challenging example is negative gas adsorption (NGA).

To completely describe the thermodynamics of responsive frameworks simulations of a fully flexible solid in presence of adsorbate are necessary.
Simulations, within this osmotic ensemble provide access to the grand canonical potential ($\Omega$).
This potential completely describes the thermodynamic features of the system with respect to the energies of the framework, the chemical potential of the adsorbed fluid, external pressure and temperature.
Atomistic simulations within the osmotic ensemble remain challenging because dynamics must be combined with particle insertion/deletion, which has only been applied to handful of systems.

Analysis of the grand canonical potential are often achieved using analytical descriptions of gas adsorption.
This has been particularly insightful the relative stability of two distinct and porous phases.
For example, the process of ``breathing'' can be directly seen for two different porous phases based on the difference in grand canonical potential, $\Omega$ (Figure~\ref{fgr:figure1}a,b).

In the present work we have employed state-of-the-art molecular simulations to produce a detailed picture of the entire landscape of grand canonical potential for changes in pressure, amount adsorbed and cell volume for DUT-49.
This complete thermodynamic analysis provides unprecedented insight into the phase stability under adsorption.
Our analysis recreates experimental observations, demonstrates the effects of temperature and outlines the kinetic and thermodynamics phases present during NGA.

% \begin{figure}[htb]
%   \includegraphics{../figures/figure1-01.png}
%     \caption{}
%     \label{fgr:figure1}
%   \end{figure}

Our methodology uses grand canonical Monte Carlo moves combined with molecular dynamics trajectories in the $(N,V,\sigma_{a}=0,T)$ ensemble, to effectively constraining the volume while allowing the cell shape to fluctuate. Subsequently, adsorption isotherms at each unit cell volume then are used to construct the grand canonical potential as Equation~{\ref{eqn:osmoticequation}}.

% \begin{equation}
%   \Omega\left(N_{\mathrm{host}}, p, \sigma_{a}=\mathbf{0}, T ; V\right)=F_{\mathrm{host}}\left(N_{\mathrm{host}}, T ; V\right)+p V-\int_{-\infty}^{\mu(p, T)} N_{\mathrm{guest}}\left(N_{\mathrm{host}}, \mu^{\prime}, \sigma_{a}=\mathbf{0}, T ; V\right) \mathrm{d} \mu^{\prime}
%   \label{eqn:osmoticequation}
% \end{equation}

The resulting potential at different methane gas pressures and cell volumes is displayed in Figure~\ref{fgr:figure1}c. To obtain accurate integrals of the number of adsorbed particles (third term in Equation~{\ref{eqn:osmoticequation}}), a large number of chemical potentials were considered.

This detailed potential landscape contains metastable and equilibrium states that change with  increasing gas pressure (Figure~\ref{fgr:figure2}). The system, at zero gas pressure, begins at equilibrium in the $op$ phase (large cell volume) where there is also a metastable $cp$ phase (small cell volume. The observed states correspond are in quantitative agreement with in situ studies.
Intermediate phases, between the $op$ and $cp$ phases, are observed by simulation and experiment further highlighting the accuracy of our proposed landscape.

  % \begin{figure}[htb]
  %   \includegraphics{../figures/figure2-01.png}
  %     \caption{}
  %     \label{fgr:figure2}
  %   \end{figure}

Simulations were completed for three temperatures (90$\,$K, 120$\,$ and 150$\,$) to provide insight to the thermodynamic trends responsible for the observations of different phases for DUT-49.
Particularly, temperature demonstrates a fascinating non-monotonic relationship with amount of gas released during the negative gas adsorption process.
The relative grand potential between the $op$ and $cp$ phases can be directly computed from these simulations, in addition to the energy barrier between these states (Figure~\ref{fgr:figure3}a). It is observed that the pressure window for stability of the $cp$ phase is correlated with temperature, due to the entropic effects of condensing gas to a smaller pore structure.
The maximum energy difference is also correlated with temperature.
Contrastingly, the minimum barrier height shows a weaker trend with temperature.
A temperature of 90 and 120$\,$K shows no energy barrier between the states.
We can alternatively consider these trends with respect to the difference in  adsorbed amount in the $op$ and $cp$ phases ((Figure~\ref{fgr:figure3}b), which represents the magnitude of negative gas adsorption. 
Interestingly, the $cp$ phase can become more favorable than the $op$ phase before the crossing point of the individual isotherms, represent by 0.
This is especially true for the.

%     \begin{figure}[htb]
%       \includegraphics{../figures/figure3-01.png}
%         \caption{}
%         \label{fgr:figure3}
%       \end{figure}

% The finally.

%       \begin{figure*}[htb]
%         \includegraphics{../figures/figure4-01.png}
%           \caption{}
%           \label{fgr:figure4}
%         \end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "Acknowledgement" section can be given in all manuscript
%% classes.  This should be given within the "acknowledgement"
%% environment, which will make the correct section or running title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgement}
  J. D. E. acknowledges the support of the Alexander von Humboldt foundation and HPC platforms provided by a GENCI grant (A0070807069) and the Center for Information Services and High Performance Computing (ZIH) at TU Dresden.
\end{acknowledgement}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The same is true for Supporting Information, which should use the
%% suppinfo environment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{suppinfo}

% This will usually read something like: ``Experimental procedures and
% characterization data for all new compounds. The class will
% automatically add a sentence pointing to the information on-line:

% \end{suppinfo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The appropriate \bibliography command should be placed here.
%% Notice that the class file automatically sets \bibliographystyle
%% and also names the section correctly.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{article}

\end{document}

### 2020-09-02 readaif_getBETarea.py

@@ -1,0 +1,164 @@
+import numpy as np
+from gemmi import cif
+
+aif = cif.read_file('database/DUT-60/ih_DUT-60_183b.aif')
+block = aif.sole_block()
+ads_press = np.array(block.find_loop('_adsorption_pressure'),dtype=float)
+ads_amount = np.array(block.find_loop('_adsorption_amount'),dtype=float)
+des_press = np.array(block.find_loop('_desorption_pressure'),dtype=float)
+des_amount = np.array(block.find_loop('_desorption_amount'),dtype=float)
+
+material_id = block.find_pair('_material_id')[-1]
+material_mass = block.find_pair('_sample_mass')[-1]
+print(material_id)
+
+#convert to mol/g to cm3/g
+ads_amount=ads_amount*0.001
+#ads_amount = ads_amount / 4.5e-3
+# ads_amount = ads_amount*float(material_mass)
+# ads_amount = ads_amount*1e-6
+
+
+#n2 properties
+p0 = 101860.98004799998
+ads_cross = 0.162
+
+pp0=ads_press/p0
+
+roq_consistency = ads_amount*(1-pp0)
+
+import matplotlib.pyplot as plt
+print(np.argmax(roq_consistency))
+plt.plot(roq_consistency, 'o-')
+plt.show()
+
+lo_limit = 0
+hi_limit= np.argmax(roq_consistency)
+
+# plt.plot(pp0[lo_limit:hi_limit],roq_consistency[lo_limit:hi_limit], 'o-')
+# plt.show()
+
+#transform to limits
+
+pp0 =  pp0[lo_limit:hi_limit]
+roq_consistency = roq_consistency[lo_limit:hi_limit]
+BETeq = pp0/roq_consistency
+
+
+
+plt.plot(pp0,BETeq,'o-')
+plt.show()
+
+from scipy.stats import linregress
+
+def rolling_window(a, window):
+    shape = a.shape[:-1] + (a.shape[-1] - window + 1, window)
+    strides = a.strides + (a.strides[-1],)
+    return np.lib.stride_tricks.as_strided(a, shape=shape, strides=strides)
+
+BETeq_window = rolling_window(BETeq,3)
+pp0_window = rolling_window(pp0,3)
+
+
+
+output = []
+for window in range(len(BETeq_window)):
+    c=[]
+    slope=[]
[…]

### 2020-09-02 readaif_getBETarea_updated.py

@@ -1,0 +1,132 @@
+import numpy as np
+from gemmi import cif
+
+aif = cif.read_file('database/DUT-75/US_540_DUT75_N2.aif')
+block = aif.sole_block()
+ads_press = np.array(block.find_loop('_adsorption_pressure'),dtype=float)
+ads_amount = np.array(block.find_loop('_adsorption_amount'),dtype=float)
+des_press = np.array(block.find_loop('_desorption_pressure'),dtype=float)
+des_amount = np.array(block.find_loop('_desorption_amount'),dtype=float)
+
+material_id = block.find_pair('_material_id')[-1]
+material_mass = block.find_pair('_sample_mass')[-1]
+print(material_id)
+
+#convert to mol/g from cm3/g
+ads_amount=ads_amount*0.001
+#ads_amount = ads_amount / 4.5e-3
+# ads_amount = ads_amount*float(material_mass)
+# ads_amount = ads_amount*1e-6
+
+
+#n2 properties
+p0 = 101860.98004799998
+ads_cross = 0.162
+
+pp0=ads_press/p0
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+from scipy.stats import linregress
+
+def rolling_window(a, window):
+    shape = a.shape[:-1] + (a.shape[-1] - window + 1, window)
+    strides = a.strides + (a.strides[-1],)
+    return np.lib.stride_tricks.as_strided(a, shape=shape, strides=strides)
+
+
+def BETanalysis(pp0, ads):
+    
+    #N2 properties
+    ads_cross = 0.162
+
+    #roq consistency criteria
+    roq_consistency = ads_amount*(1-pp0)
+
+    #set limits until maximum
+    lo_limit = 0
+    hi_limit= np.argmax(roq_consistency)
+
+    #transform to limits
+    pp0_limited =  pp0[lo_limit+1:hi_limit]
+    roq_consistency_limited = roq_consistency[lo_limit+1:hi_limit]
+
+    #compute BET equation
+    BETeq = pp0_limited/roq_consistency_limited
+
+    #separate into 3-point windowss
+    BETeq_window = rolling_window(BETeq,3)
+    pp0_window = rolling_window(pp0_limited,3)
+
+    #get slope and BET parameters
+    output = []
[…]

### 2020-11-25 manuscript/article.tex
drafting

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jacsat,manuscript=communication]{achemso}
+\documentclass[journal=langd5,manuscript=article]{achemso}
 
@@
 \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\usepackage{lineno}
+\usepackage{booktabs}
 
+\linenumbers
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand*\mycommand[1]{\texttt{\emph{#1}}}
+\renewcommand{\arraystretch}{1.2}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Ruben Goeminne}
-\affiliation[TU Ghent]
-{Center for Molecular Modeling
-Ghent University
-Tech Lane Ghent Science Park Campus A, 9052 Zwijnaarde, Belgium}
-
-\author{Simon Krause}
-\affiliation[University of Groningen]
-{Stratingh Institute for Chemistry
-Faculty of Mathematics and Natural Sciences
-University of Groningen
-Nijenborgh 4, 9747 AG Groningen, The Netherlands}
-
-\author{Toon Verstraelen}
-\affiliation[TU Ghent]
-{Center for Molecular Modeling
-Ghent University
-Tech Lane Ghent Science Park Campus A, 9052 Zwijnaarde, Belgium}
-\email{toon.verstraelen@ugent.be}
 
@@
 
+\author{Stefan Kaskel}
+\affiliation[TU Dresden]
+{Department of inorganic chemistry
+Technische Universität Dresden
+Bergstraße 66, 01062 Dresden, Germany}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \title[]
-  {Mapping the complete thermodynamic landscape of gas adsorption for a responsive metal-organic framework}
+  {A universal standard archive file for adsorption data}
 
@@
 \begin{abstract}
-  To do.
+  The rise in interest of new advanced adsorbents for application in promising areas has followed a lack of detailed and open reporting of experimental or even computational studies.
+  This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
+  The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable --- simple to edit using a basic text editor or parse for database curation.
+  This format represents the first steps to an open adsorption data format.
+  An open format sorely needed for the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials.
 \end{abstract}
@@
 \section{Introduction}
+It is important in many branches of science for there to exist a uniform and flexible method of archiving and exchanging data.
+The data presented in research contributions must be readily accessible and easily verifiable.
+Key to scientific discovery and innovation the use of good data management practices can  provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1038/sdata.2016.18}
+Unfortunately, the existing ecosystem surrounding scholarly data publication often prevent the community extracting maximum benefit from published research.
+This lead to the foundational principles discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
 
-Advanced porous materials are poised for application.
+Porous solids are of important scientific and industrial interest owing to their impressive ability to interact with all manner of atoms, ions and molecules throughout the entirety of the solid, not only the surface.\cite{}
+This has led to many exciting applications of , traditional applications of porous materials thus involve ion exchange, adsorption (for separation) and catalysis, and many of these benefit from the high order that can be achieved in solids such as zeolites.\cite{}
 
-It is often the flexibility of porous adsorbents that enables unparalleled performance in separation applications.
+Measuring the interaction of gas with porous materials is crucial to understanding and comparing the plethora of different materials.
+The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, it is recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.
+If possible, the composition of the adsorbent should be specified and its surface characterised.
+To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphica form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive.
+If the adsorption measurements are made under conditions where the gas phase deviates appreciably from ideality (e.g., at high pressure), it is desirable that the isotherms should be presented in terms of gas fugacity rather than pressure.
 
-Responsive adsorbents, such as metal-organic frameworks, can significantly change pore structure and volume in response to stimuli.\cite{10.1021/acs.chemmater.5b00046}
+Rapid advances in computer technology, coupled with the expansion of local, national and international networks, have fuelled the need for such a facility.
+The variety and relative inflexibility of existing data exchange formats have inhibited their ef- fective use.
+This is true even in fields where the basic data requirements are well defined.
+Problems of data ex- changearefurtherexacerbatedif thenumberandnatureof data types change rapidly and continuously.
+Under these conditions specialized and local file formats have prolif- erated.
+This diversity was tolerable when electronic data transfer was infrequent, or when data processing speeds required file formats finely tuned to specific applications.
+The developments cited above signal an end to this ration- ale.
+A general, flexible, rapidly extensible and universal file format protocol is now essential.It must be machine- independent and portable so that accessibility to data items is independent of their point of origin.
+It must allow new data items to be incorporated without the need to modify existing files.
+Since the development of the first porous materials, there has been a sharp rise in the design of highly ordered and structured porous materials (Fig.
+S1).
+The advent of materials with more complex pore networks and dynamic frameworks through materials design strategies such as reticular chemistry has given rise to reported BET areas in excess of 8,000 m2 g1.[11,2528] Often, these complex materials have complex adsorption isotherms which have become harder to fit into the BET model.
+In response to these advances, materials scientists have developed a new generation of porosimetry equipment with pressure transducers capable of the collection of high-resolution gas adsorption isotherms at ultra-low pressures (<10-5 mmHg).
+Despite these advances, scientists still rely on the manual calculation of surface areas using BET theory
 
-One particularly challenging example is negative gas adsorption (NGA).
+\section{AIF structure and syntax}
+The information contained within an AIF is arranged in a strict structural arrangement.
+Alternative data storage structures were considered, during the development the AIF,  such as the comma-separated-value (CSV) file.
+The key, however, is that a universal data format must also include a well-structured record of metadata associated with the adsorption experiment.
+Without the metadata of, containing at the very least, what gas or temperature was used during the experiment the resulting adsorption data is meaningless.
+Metadata is also important in the development of databases.
+This is crucial to identify identical or related data, understand the evolution of databases over time, and also permit further examination for specific data items.
+As a result the STAR data structure was adopted, which is famously used in the crystallographic information file (CIF) and biological nuclear magnetic resonance experiments (NMR-STAR).
+An important property of the STAR format is that its syntax is defined by a few simple rules using an object/relational model.
+The data stored in a STAR file is self-descriptive as the underpinning data structure consists of tag-value pairs or data item.
+This data item is the combination a data value with the data name, an identifying unique tag.
+This approach is flexible and able to represent.
+nested and repetitive data, which are particularly important for the collection of pressure and adsorbed amount that comprise an adsorption isotherm experiment.
 
-To completely describe the thermodynamics of responsive frameworks simulations of a fully flexible solid in presence of adsorbate are necessary.
-Simulations, within this osmotic ensemble provide access to the grand canonical potential ($\Omega$).
-This potential completely describes the thermodynamic features of the system with respect to the energies of the framework, the chemical potential of the adsorbed fluid, external pressure and temperature.
-Atomistic simulations within the osmotic ensemble remain challenging because dynamics must be combined with particle insertion/deletion, which has only been applied to handful of systems.
+The data structure of an AIF is comprised of comment lines and data blocks, which contains the required metadata and quantities related to the adsorption experiment, separated for adsorption and desorption (Figure~\ref{fgr:datastructure}).
+Files can contain any number of data blocks to represent multiple experiments.
+Fundamentally, a data block is a data cell containing a sequence of data items, data loops.
+It starts with a data block code statement (\texttt{data\_example}) where a block code is a unique identifying code with in a file.
+A data block is closed by another either another data block code statement or the end of file.
+Comment lines can be placed anywhere in the file and are identified by a hash (\texttt{\#}) symbol.
+As these comment lines do not necessarily represent structured data, which is able to be easily parsed, it is not recommended to solely include important experimental conditions in this way.
+Single values or strings can be included within a data block using the data name and data value pairs.
+Data values are preceded by an identifying data name that is identify by an underscore character, for example \texttt{\_temperature}.
+A data loop structure consists of a loop statement (\texttt{loop\_}) followed by a list of data names and then a list of data, each of which contains data values that matches the data names in the list of data names.
+Though data loops can be nested at any level this is not necessary for the current implementation.
+Importantly, data values that follow the nested data declarations must be in exact multiples of the number of data names (which are referred to as loop packets).
+The data loops, as used here, are terminated by a new data item, a new data loop or an end of file.
+These data loops can thus straightforwardly represent the data recorded at each point of an adsorption and desorption experiment, for example the pressure and quantities adsorbed.
 
-Analysis of the grand canonical potential are often achieved using analytical descriptions of gas adsorption.
-This has been particularly insightful the relative stability of two distinct and porous phases.
-For example, the process of ``breathing'' can be directly seen for two different porous phases based on the difference in grand canonical potential, $\Omega$ (Figure~\ref{fgr:figure1}a,b).
+  \begin{figure}[htb]
+    \includegraphics{./figures/structure-01.png}
+      \caption{The structure of a typical adsorption information file (AIF) with the different data areas representing metadata (experimental and sample information) and the adsorption and desorption data.}
+      \label{fgr:datastructure}
+    \end{figure}
 
-In the present work we have employed state-of-the-art molecular simulations to produce a detailed picture of the entire landscape of grand canonical potential for changes in pressure, amount adsorbed and cell volume for DUT-49.
-This complete thermodynamic analysis provides unprecedented insight into the phase stability under adsorption.
-Our analysis recreates experimental observations, demonstrates the effects of temperature and outlines the kinetic and thermodynamics phases present during NGA.
+The above data structures of the STAR format prove ideal for describing the detailed quantities relating to an adsorption experiment.
+An entire experiment can be described within a single data block.
+Initially, data name and data value pairs can be used to identify quantities relating to the whole experiment such as the date and time, temperature and adsorptive.
+The data points for the adsorption and desorption branch can then be detailed in separate data loops.
+For each point, quantities such as the absolute pressure, relative pressure and amount adsorbed can be detailed.
+This leads us to the general data structure for the AIF (Figure~\ref{fgr:datastructure}).
 
-% \begin{figure}[htb]
-%   \includegraphics{../figures/figure1-01.png}
-%     \caption{}
-%     \label{fgr:figure1}
-%   \end{figure}
+\section{AIF dictionary}
+Each data item within a data block is identified using a unique data name.
+The currently accepted AIF data names are listed and defined in Table~\ref{tbl:example}.
+These data items form a first version of a core dictionary, which are intended for primarily reporting primary physisorption data for gas on porous materials.
+As a result the dictionary contains information about crucial experimental parameters, basic sample characterization, adsorption and desorption measures, each distinguished by a data name prefix (\texttt{\_exptl\_}, \texttt{\_sample\_}, \texttt{\_adsorp\_} and \texttt{\_desorp\_}).
 
-Our methodology uses grand canonical Monte Carlo moves combined with molecular dynamics trajectories in the $(N,V,\sigma_{a}=0,T)$ ensemble, to effectively constraining the volume while allowing the cell shape to fluctuate.
-Subsequently, adsorption isotherms at each unit cell volume then are used to construct the grand canonical potential as Equation~{\ref{eqn:osmoticequation}}.
+\begin{table}
+  \caption{Core dictionary of data items}
+  \label{tbl:example}
+  \begin{tabular}{@{}ll@{}}
+    \toprule
+    data name & description  \\
+    \midrule
+    \texttt{\_exptl\_operator}  & name of the person who ran the experiment (string)  \\
+    \texttt{\_exptl\_date} & date and time of the experiment (datetime string representation) \\
+    \texttt{\_exptl\_instrument}  & instrument id used for the experiment (string)  \\
+    \texttt{\_exptl\_adsorptive}  & name of the adsorptive (string)  \\
+    \texttt{\_exptl\_temperature}  & temperature of the experiment (float)  \\
+    \texttt{\_exptl\_sample\_mass}  & mass of the sample (float, gram) \\
+    \texttt{\_sample\_id}  & unique identifying code used by the operator (string)\\
+    \texttt{\_sample\_material\_name}  & designated name for the material (string) \\
+    \texttt{\_adsorp\_pressure} & pressure of the adsorption measurement (float, pascal)\\
+    \texttt{\_adsorp\_p0} & saturation pressure of the adsorption measurement (float, pascal) \\
+    \texttt{\_adsorp\_amount} & amount adsorbed during the adsorption measurement (float, mol$\,$kg$^{-1}$) \\
+    \texttt{\_desorp\_pressure} & pressure of the desorption measurement (float, pascal) \\
+    \texttt{\_desorp\_p0} & saturation pressure of the desorption measurement (float, pascal) \\
+    \texttt{\_desorp\_amount} & amount adsorbed during the desorption measurement (float, mol$\,$kg$^{-1}$) \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The goal of the experimental data names is to capture the information required to accurately portray the results of experiment, which at the very minimum are the temperature and adsorptive.
+As metadata should include information that may aid in identifying possible errors this also includes the mass of sample used in the experiment.
+Additionally, data is included relative to the date, time and person responsible for the measurement to produce a general picture of the provenance of the experiment.
+
+Details of the sample are recorded for comparison and to uniquely identify the sample that was used in the experiment.
+Simply, this includes the sample identity code (\texttt{\_sample\_id}), a laboratory code used to record and represent the sample and a string relating to the general designation given to the material (\texttt{\_sample\_material\_name}).
+
+For each data point measured during an adsorption experiments data can be stored that relates to the equilibrated pressure, the saturation pressure and the amount adsorbed.
+Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.
+The saturation pressure can be recorded at each data point as we have discovered that some instruments will calculate and report this value for every point.
+
+The above features serve as an example of the data that can be archived in a AIF and can be extended in future versions.
+For example, the intention of this initial version is to provide digital archive of the presented primary data of an adsorption experiment, the isotherm.
+As a result, it describes only basic information that usually exported from adsorption instruments and a few convenient metadata items.
+The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements, or combined with CIF data names to archive in situ measurements.
+
+\section{Creating and using the AIF}
+A simple python 3.7 routine was produced during the development of the AIF to convert the plain text data output from Quantachrome and Belsorb instruments, used in our lab and many others.
+Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (.DAT) and csv files exported by Belsorb software.
+At this moment we are unable to read binary data files that are saved by Quatachrome instruments (.qps).
+
+This simple program will parse the output data to find data items detailed in the AIF dictionary.
+These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
+Subsequently an AIF is produced using the pymatgen CIF routines.
+This demonstrated that routines and methods developed for treating CIF files can be used in this application to adsorption data.
+Furthermore, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python module, which we have used to demonstrate how an isotherm can be displayed from an AIF using a few lines.
+This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in to routines to parse the information directly from binary data used by the instruments.
+
+To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
+The porous material DUT-6 (also referred to as MOF-206) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
+DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
+The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~/ref{fgr:example}).
+From this plot the isotherm can be classified  as  type  Ib clearly exhibiting characteristics of a hierarchal pore system with micropore and mesopores.
+Clearly there is a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
+The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.
+The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
+In this methodology each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data valued based on an axes calibration.
+The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information is lost when this information is simply included as a figure in a manuscript (Figure~/ref{fgr:example}).
+To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers adsorption data should be archived and shared using the a universal and complete data format like that of the AIF.
+
+  \begin{figure}[htb]
+    \includegraphics{./figures/example-01.png}
+      \caption{The reported nitrogen adsorption isotherm of DUT-6 recorded at 77$\,$K (a).
+A digitized representation of this reported isotherm was achieved using a point-picking method (b) and compared to the experimental data as contained within an AIF (c).}
+      \label{fgr:example}
+    \end{figure}
+
+\section{Summary and perspective}
+The
 
@@
 
-The resulting potential at different methane gas pressures and cell volumes is displayed in Figure~\ref{fgr:figure1}c.
-To obtain accurate integrals of the number of adsorbed particles (third term in Equation~{\ref{eqn:osmoticequation}}), a large number of chemical potentials were considered.
-
-This detailed potential landscape contains metastable and equilibrium states that change with  increasing gas pressure (Figure~\ref{fgr:figure2}).
-The system, at zero gas pressure, begins at equilibrium in the $op$ phase (large cell volume) where there is also a metastable $cp$ phase (small cell volume.
-The observed states correspond are in quantitative agreement with in situ studies.
-Intermediate phases, between the $op$ and $cp$ phases, are observed by simulation and experiment further highlighting the accuracy of our proposed landscape.
-
   % \begin{figure}[htb]
@@
   %   \end{figure}
-
-Simulations were completed for three temperatures (90$\,$K, 120$\,$ and 150$\,$) to provide insight to the thermodynamic trends responsible for the observations of different phases for DUT-49.
-Particularly, temperature demonstrates a fascinating non-monotonic relationship with amount of gas released during the negative gas adsorption process.
-The relative grand potential between the $op$ and $cp$ phases can be directly computed from these simulations, in addition to the energy barrier between these states (Figure~\ref{fgr:figure3}a).
-It is observed that the pressure window for stability of the $cp$ phase is correlated with temperature, due to the entropic effects of condensing gas to a smaller pore structure.
-The maximum energy difference is also correlated with temperature.
-Contrastingly, the minimum barrier height shows a weaker trend with temperature.
-A temperature of 90 and 120$\,$K shows no energy barrier between the states.
-We can alternatively consider these trends with respect to the difference in  adsorbed amount in the $op$ and $cp$ phases ((Figure~\ref{fgr:figure3}b), which represents the magnitude of negative gas adsorption.
-Interestingly, the $cp$ phase can become more favorable than the $op$ phase before the crossing point of the individual isotherms, represent by 0.
-This is especially true for the.
-
-%     \begin{figure}[htb]
-%       \includegraphics{../figures/figure3-01.png}
-%         \caption{}
-%         \label{fgr:figure3}
-%       \end{figure}
-
-% The finally.
-
-%       \begin{figure*}[htb]
-%         \includegraphics{../figures/figure4-01.png}
-%           \caption{}
-%           \label{fgr:figure4}
-%         \end{figure*}
 

### 2020-11-25 example/compareaif.py

@@ -1,0 +1,47 @@
+import numpy as np
+from gemmi import cif
+
+
+
+aif = cif.read_file('example/nk_DUT-6_LP_N2_114pkt.aif')
+block = aif.sole_block()
+ads_press = np.array(block.find_loop('_adsorp_pressure'),dtype=float)
+ads_p0 = np.array(block.find_loop('_adsorp_p0'),dtype=float)
+ads_amount = np.array(block.find_loop('_adsorp_amount'),dtype=float)
+des_press = np.array(block.find_loop('_desorp_pressure'),dtype=float)
+des_p0 = np.array(block.find_loop('_desorp_p0'),dtype=float)
+des_amount = np.array(block.find_loop('_desorp_amount'),dtype=float)
+
+
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+
+mpl.rcParams['pdf.fonttype'] = 42
+
+plt.rcParams.update({'font.size': 6})
+
+f, (ax1, ax2) = plt.subplots(1, 2, sharey=True, sharex=True)
+
+f.tight_layout()
+f.set_size_inches(3,2.2)
+
+ax2.semilogx(ads_press/ads_p0,ads_amount, 'o', color='tab:blue')
+ax2.plot(des_press/des_p0,des_amount, 'o', markerfacecolor='white', color='tab:blue')
+
+digit_ads_press = np.genfromtxt("example/Default Dataset.csv", delimiter=',')[:,0]
+digit_ads_amount = np.genfromtxt("example/Default Dataset.csv", delimiter=',')[:,1]
+
+digit_des_press = np.genfromtxt("example/Default Dataset2.csv", delimiter=',')[:,0]
+digit_des_amount = np.genfromtxt("example/Default Dataset2.csv", delimiter=',')[:,1]
+
+#convert units
+digit_ads_amount = digit_ads_amount/22.414
+digit_des_amount = digit_des_amount/22.414
+
+ax1.semilogx(digit_ads_press,digit_ads_amount , 'o', color='tab:orange')
+ax1.semilogx(digit_des_press,digit_des_amount , 'o', markerfacecolor='white', color='tab:orange')
+
+ax1.set_ylabel("amount adsorbed / mol$\,$kg$^{-1}$")
+ax2.set_xlabel(r'relative pressure / $p/p_0$')
+
+plt.savefig('example/exampleplot.pdf', dpi=600, bbox_inches='tight')

### 2020-11-25 raw2aif.py

@@ -243,27 +243,27 @@ from monty.io import zopen
 block = OrderedDict()
 loops = []
 
-block["_operator"] = operator
-block["_date"] = date
-block["_instrument"] = instrument
-block["_adsorptive"] = adsorptive
-block["_temperature"] = temperature
-block["_sample_mass"] = sample_mass
+block["_exptl_operator"] = operator
+block["_exptl_date"] = date
+block["_exptl_instrument"] = instrument
+block["_exptl_adsorptive"] = adsorptive
+block["_exptl_temperature"] = temperature
+block["_exptl_sample_mass"] = sample_mass
 block["_sample_id"] = sample_id
-block["_material_id"] = material_id
+block["_sample_material_id"] = material_id
 
-block["_adsorption_pressure"] = ads_press
-block["_adsorption_p0"] = ads_p0
-block["_adsorption_amount"] = ads_vol
+block["_adsorp_pressure"] = ads_press
+block["_adsorp_p0"] = ads_p0
+block["_adsorp_amount"] = ads_vol
 
-loops.append(["_adsorption_pressure","_adsorption_p0", "_adsorption_amount"])
+loops.append(["_adsorp_pressure","_adsorp_p0", "_adsorp_amount"])
 
 
-block["_desorption_pressure"] = des_press
-block["_desorption_p0"] = des_p0
-block["_desorption_amount"] = des_vol
+block["_desorp_pressure"] = des_press
+block["_desorp_p0"] = des_p0
+block["_desorp_amount"] = des_vol
 
-loops.append(["_desorption_pressure","_desorption_p0", "_desorption_amount"])
+loops.append(["_desorp_pressure","_desorp_p0", "_desorp_amount"])
 
 d = OrderedDict()
 header = "raw2ciftest"

### 2020-11-25 readaif.py

@@ -3,10 +3,10 @@ from gemmi import cif
 
 aif = cif.read_file('database/DUT-6/nk_DUT-6_LP_N2_114pkt.aif')
 block = aif.sole_block()
-ads_press = np.array(block.find_loop('_adsorption_pressure'),dtype=float)
-ads_amount = np.array(block.find_loop('_adsorption_amount'),dtype=float)
-des_press = np.array(block.find_loop('_desorption_pressure'),dtype=float)
-des_amount = np.array(block.find_loop('_desorption_amount'),dtype=float)
+ads_press = np.array(block.find_loop('_adsorp_pressure'),dtype=float)
+ads_amount = np.array(block.find_loop('_adsorp_amount'),dtype=float)
+des_press = np.array(block.find_loop('_desorp_pressure'),dtype=float)
+des_amount = np.array(block.find_loop('_desorp_amount'),dtype=float)
 
 material_id = block.find_pair('_material_id')[-1]
 print(material_id)

### 2020-11-26 manuscript/article.tex
intro drafted

@@
 
-Measuring the interaction of gas with porous materials is crucial to understanding and comparing the plethora of different materials.
-The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, it is recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.
-If possible, the composition of the adsorbent should be specified and its surface characterised.
-To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphica form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive.
+Measuring the interaction of gas with a material is crucial to understanding and comparing the plethora of different porous materials.
+The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{} Moreover, if possible, the composition of the adsorbent should be specified and its surface characterized.
+To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive.
 If the adsorption measurements are made under conditions where the gas phase deviates appreciably from ideality (e.g., at high pressure), it is desirable that the isotherms should be presented in terms of gas fugacity rather than pressure.
 
-Rapid advances in computer technology, coupled with the expansion of local, national and international networks, have fuelled the need for such a facility.
-The variety and relative inflexibility of existing data exchange formats have inhibited their ef- fective use.
-This is true even in fields where the basic data requirements are well defined.
-Problems of data ex- changearefurtherexacerbatedif thenumberandnatureof data types change rapidly and continuously.
-Under these conditions specialized and local file formats have prolif- erated.
-This diversity was tolerable when electronic data transfer was infrequent, or when data processing speeds required file formats finely tuned to specific applications.
-The developments cited above signal an end to this ration- ale.
-A general, flexible, rapidly extensible and universal file format protocol is now essential.It must be machine- independent and portable so that accessibility to data items is independent of their point of origin.
+Rapid advances in computer simulations, coupled with the expansion of fruitful local, national and international networks, have fueled the need for a standardization of adsorption data.
+The variety and relative inflexibility of existing adsorption data formats can inhibit the effective use of reported data.
+A general, flexible, rapidly extensible and universal file format protocol is essential to further accelerate the developed of porous materials.
+As with other standard formats, this must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
 It must allow new data items to be incorporated without the need to modify existing files.
-Since the development of the first porous materials, there has been a sharp rise in the design of highly ordered and structured porous materials (Fig.
-S1).
-The advent of materials with more complex pore networks and dynamic frameworks through materials design strategies such as reticular chemistry has given rise to reported BET areas in excess of 8,000 m2 g1.[11,2528] Often, these complex materials have complex adsorption isotherms which have become harder to fit into the BET model.
-In response to these advances, materials scientists have developed a new generation of porosimetry equipment with pressure transducers capable of the collection of high-resolution gas adsorption isotherms at ultra-low pressures (<10-5 mmHg).
-Despite these advances, scientists still rely on the manual calculation of surface areas using BET theory
 

### 2020-11-27 manuscript/article.tex
introduction finished

@@
 
+\author{Volodymyr Bon}
+\affiliation[TU Dresden]
+{Department of inorganic chemistry
+Technische Universität Dresden
+Bergstraße 66, 01062 Dresden, Germany}
+
+\author{Irena Senkovska}
+\affiliation[TU Dresden]
+{Department of inorganic chemistry
+Technische Universität Dresden
+Bergstraße 66, 01062 Dresden, Germany}
+
 \author{Stefan Kaskel}
@@
   This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
-  The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable --- simple to edit using a basic text editor or parse for database curation.
+  The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
   This format represents the first steps to an open adsorption data format.
@@
 The data presented in research contributions must be readily accessible and easily verifiable.
-Key to scientific discovery and innovation the use of good data management practices can  provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1038/sdata.2016.18}
-Unfortunately, the existing ecosystem surrounding scholarly data publication often prevent the community extracting maximum benefit from published research.
-This lead to the foundational principles discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
+Key to scientific discovery and innovation the use of good data management practices can  provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1002/adts.201900131}
+Unfortunately, the existing ecosystem surrounding scholarly data publication often prevents the research community extracting maximum benefit from published reports.
+This led to the foundational principles as discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
 
-Porous solids are of important scientific and industrial interest owing to their impressive ability to interact with all manner of atoms, ions and molecules throughout the entirety of the solid, not only the surface.\cite{}
-This has led to many exciting applications of , traditional applications of porous materials thus involve ion exchange, adsorption (for separation) and catalysis, and many of these benefit from the high order that can be achieved in solids such as zeolites.\cite{}
+Porous solids are of important scientific and industrial interest owing to their impressive ability to interact with all manner of atoms, ions and molecules throughout the entirety of the solid, not only the surface.\cite{10.1038/nature00785}
+This has led to many exciting applications for porous materials, including ion exchange, gas storage, separations and catalysis.\cite{10.1039/C6CS00135A}
+Measuring the interaction of gas with a material is crucial to understanding and comparing different porous materials.
+The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{10.1515/pac-2014-1117}
+To facilitate the comparison of adsorption data, the IUPAC also recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$ plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the experiment temperature, or when the temperature is above the critical temperature of the adsorbing gas, against absolute pressure.
 
-Measuring the interaction of gas with a material is crucial to understanding and comparing the plethora of different porous materials.
-The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{} Moreover, if possible, the composition of the adsorbent should be specified and its surface characterized.
-To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive.
-If the adsorption measurements are made under conditions where the gas phase deviates appreciably from ideality (e.g., at high pressure), it is desirable that the isotherms should be presented in terms of gas fugacity rather than pressure.
+Rapid advances in computer simulations, coupled with the expansion of fruitful local, national and international networks, have fueled the need for a standardization of adsorption data beyond the current IUPAC recommendations.
+The variety and relative inflexibility of existing adsorption data formats and conventional graphical reporting inhibits the effective use of reported data.
+A general, flexible, rapidly extensible and universal file format protocol following the guidelines presented by Wilkinson et al.
+is essential to further accelerate the development of porous materials.
+As with other standard formats, this must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
+It must also allow new data items to be incorporated without the need to modify existing files to enable an evolving format.
 
-Rapid advances in computer simulations, coupled with the expansion of fruitful local, national and international networks, have fueled the need for a standardization of adsorption data.
-The variety and relative inflexibility of existing adsorption data formats can inhibit the effective use of reported data.
-A general, flexible, rapidly extensible and universal file format protocol is essential to further accelerate the developed of porous materials.
-As with other standard formats, this must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
-It must allow new data items to be incorporated without the need to modify existing files.
+In this submission we outline our proposal for a new standard adsorption information file (AIF) and the clear advantages of this format compared to the currently accepted graphical deposition method.
+The AIF is free-format archive file that is readily human and machine readable, both simple to edit using a basic text editor or parse using computer programs.
+This represents the first flexible, general and easily extended format for representing the results of adsorption experiments and the first steps towards standardizing a format for archiving adsorption data.
 
@@
 This is crucial to identify identical or related data, understand the evolution of databases over time, and also permit further examination for specific data items.
-As a result the STAR data structure was adopted, which is famously used in the crystallographic information file (CIF) and biological nuclear magnetic resonance experiments (NMR-STAR).
+As a result the STAR data structure was adopted,\cite{10.1021/ci00019a005} which is famously used in the crystallographic information file (CIF) and biological nuclear magnetic resonance experiments (NMR-STAR).\cite{10.1107/S010876739101067X,10.1007/s10858-018-0220-3}
 An important property of the STAR format is that its syntax is defined by a few simple rules using an object/relational model.
@@
     \texttt{\_exptl\_operator}  & name of the person who ran the experiment (string)  \\
-    \texttt{\_exptl\_date} & date and time of the experiment (datetime string representation) \\
+    \texttt{\_exptl\_date} & date and time of the experiment (date-time string representation) \\
     \texttt{\_exptl\_instrument}  & instrument id used for the experiment (string)  \\
@@
 For each data point measured during an adsorption experiments data can be stored that relates to the equilibrated pressure, the saturation pressure and the amount adsorbed.
-Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.
+Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.\cite{10.1515/pac-2014-1117}
 The saturation pressure can be recorded at each data point as we have discovered that some instruments will calculate and report this value for every point.
@@
 A simple python 3.7 routine was produced during the development of the AIF to convert the plain text data output from Quantachrome and Belsorb instruments, used in our lab and many others.
-Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (.DAT) and csv files exported by Belsorb software.
-At this moment we are unable to read binary data files that are saved by Quatachrome instruments (.qps).
+Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (\textit{.DAT}) and CSV files exported by Belsorb software.
+At this moment we are unable to read binary data files that are saved by Quatachrome instruments (\textit{.qps}).
 
@@
 These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
-Subsequently an AIF is produced using the pymatgen CIF routines.
+Subsequently an AIF is produced using the pymatgen CIF routines.\cite{10.1016/j.commatsci.2012.10.028}
 This demonstrated that routines and methods developed for treating CIF files can be used in this application to adsorption data.
-Furthermore, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python module, which we have used to demonstrate how an isotherm can be displayed from an AIF using a few lines.
+Furthermore, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
+We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
 This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in to routines to parse the information directly from binary data used by the instruments.
@@
 In this methodology each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data valued based on an axes calibration.
-The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information is lost when this information is simply included as a figure in a manuscript (Figure~/ref{fgr:example}).
+The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).
+
 To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers adsorption data should be archived and shared using the a universal and complete data format like that of the AIF.
@@
     \includegraphics{./figures/example-01.png}
-      \caption{The reported nitrogen adsorption isotherm of DUT-6 recorded at 77$\,$K (a).
+      \caption{The reported nitrogen adsorption isotherm of DUT-6 recorded at 77$\,$K (a) as reported in Ref.
+\citenum{10.1002/anie.200904599}.
 A digitized representation of this reported isotherm was achieved using a point-picking method (b) and compared to the experimental data as contained within an AIF (c).}
@@
 \section{Summary and perspective}
-The
+The rise in interest of new advanced adsorbents for application in promising areas has followed a lack of detailed and open reporting of experimental or even computational studies.
+This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
+The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
+This format represents the first steps to an open adsorption data format.
+An open format sorely needed for the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials.
 

### 2020-11-27 example/generateBET.py

@@ -1,0 +1,118 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+from scipy.stats import linregress
+
+def rolling_window(a, window):
+    shape = a.shape[:-1] + (a.shape[-1] - window + 1, window)
+    strides = a.strides + (a.strides[-1],)
+    return np.lib.stride_tricks.as_strided(a, shape=shape, strides=strides)
+
+
+def BETanalysis(pp0, ads):
+    
+    #N2 properties
+    ads_cross = 0.162
+
+    #roq consistency criteria
+    roq_consistency = ads_amount*(1-pp0)
+
+    #set limits until maximum
+    lo_limit = 0
+    hi_limit= np.argmax(roq_consistency)
+
+    #transform to limits
+    pp0_limited =  pp0[lo_limit+1:hi_limit]
+    roq_consistency_limited = roq_consistency[lo_limit+1:hi_limit]
+
+    #compute BET equation
+    BETeq = pp0_limited/roq_consistency_limited
+
+    #separate into 3-point windowss
+    BETeq_window = rolling_window(BETeq,3)
+    pp0_window = rolling_window(pp0_limited,3)
+
+    #get slope and BET parameters
+    output = []
+    for window in range(len(BETeq_window)):
+        c=[]
+        slope=[]
+        intercept=[]
+        fit = linregress(pp0_window[window],BETeq_window[window])
+        slope = fit[0]
+        intercept = fit[1]
+        r2 = fit[2]
+        c = 1+(slope/intercept)
+        if c > 0 and r2>0.995 and intercept > 0:
+            n_monolayer = 1/(intercept * c)
+            pp0_monolayer = 1/(np.sqrt(c) + 1)
+            BET_area = n_monolayer * ads_cross * (10**(-18)) * 6.022E23
+            output.append([c,n_monolayer,BET_area,pp0_monolayer,np.min(pp0_window[window]),np.max(pp0_window[window]),np.mean(pp0_window[window]),r2, np.abs(np.min(np.mean(pp0_window[window]-pp0_monolayer)))])
+
[…]

### 2020-11-30 manuscript/article.tex
drafting missing summary

@@
 The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~/ref{fgr:example}).
-From this plot the isotherm can be classified  as  type  Ib clearly exhibiting characteristics of a hierarchal pore system with micropore and mesopores.
-Clearly there is a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
-The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.
+From this plot the isotherm can be classified  as  type  Ib, clearly exhibiting characteristics of a hierarchal pore system with micropores and mesopores.
+There is evidently a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
+The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
 The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
-In this methodology each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data valued based on an axes calibration.
-The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).
+In this methodology, each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data values, based on an axes calibration.
+The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information, such as the point of initial pore-filling, is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).
 
-To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers adsorption data should be archived and shared using the a universal and complete data format like that of the AIF.
+To prevent this information loss and to allow further analysis of reported adsorption experiments by other researchers, adsorption data should be archived and shared using a universal and complete data format like that of the AIF.
 

### 2020-11-30 example/compareaif.py

@@ -25,8 +25,8 @@ f, (ax1, ax2) = plt.subplots(1, 2, sharey=True, sharex=True)
 f.tight_layout()
 f.set_size_inches(3,2.2)
 
-ax2.semilogx(ads_press/ads_p0,ads_amount, 'o', color='tab:blue')
-ax2.plot(des_press/des_p0,des_amount, 'o', markerfacecolor='white', color='tab:blue')
+ax2.semilogx(ads_press/ads_p0,ads_amount, 'o', color='tab:blue', ms=5)
+ax2.plot(des_press/des_p0,des_amount, 'o', markerfacecolor='white', color='tab:blue', ms=5)
 
 digit_ads_press = np.genfromtxt("example/Default Dataset.csv", delimiter=',')[:,0]
 digit_ads_amount = np.genfromtxt("example/Default Dataset.csv", delimiter=',')[:,1]
@@ -38,8 +38,8 @@ digit_des_amount = np.genfromtxt("example/Default Dataset2.csv", delimiter=',')[
 digit_ads_amount = digit_ads_amount/22.414
 digit_des_amount = digit_des_amount/22.414
 
-ax1.semilogx(digit_ads_press,digit_ads_amount , 'o', color='tab:orange')
-ax1.semilogx(digit_des_press,digit_des_amount , 'o', markerfacecolor='white', color='tab:orange')
+ax1.semilogx(digit_ads_press,digit_ads_amount , 'o', color='tab:orange', ms=5)
+ax1.semilogx(digit_des_press,digit_des_amount , 'o', markerfacecolor='white', color='tab:orange', ms=5)
 
 ax1.set_ylabel("amount adsorbed / mol$\,$kg$^{-1}$")
 ax2.set_xlabel(r'relative pressure / $p/p_0$')

### 2020-11-30 example/generateBET.py

@@ -76,7 +76,7 @@ des_amount = np.array(block.find_loop('_desorp_amount'),dtype=float)
 
 
 #convert to cm3/g to mol/g
-# ads_amount=data[:,1]/22400
+ads_amount=ads_amount/1000
 pp0=ads_press/ads_p0
 roq_consistency, lo_limit, hi_limit, pp0_limited, BETeq, results = BETanalysis(pp0,ads_amount)
 

### 2020-11-30 raw2aif.py
update raw2aif using only gemmi

@@ -235,42 +235,30 @@ sample_id = re.sub('[^a-zA-Z0-9-_*.]', '', sample_id)
 
 
 # write adsorption file
-from collections import OrderedDict
-from pymatgen.io.cif import CifBlock
-from pymatgen.io.cif import CifFile
-from monty.io import zopen
+from gemmi import cif
 
-block = OrderedDict()
-loops = []
+#initialize aif block
+d = cif.Document()
+d.add_new_block('data_raw2aif')
+block = d.sole_block()
 
-block["_exptl_operator"] = operator
-block["_exptl_date"] = date
-block["_exptl_instrument"] = instrument
-block["_exptl_adsorptive"] = adsorptive
-block["_exptl_temperature"] = temperature
-block["_exptl_sample_mass"] = sample_mass
-block["_sample_id"] = sample_id
-block["_sample_material_id"] = material_id
+#write metadata
+block.set_pair('_exptl_operator', operator)
+block.set_pair('_exptl_date', str(date))
+block.set_pair('_exptl_instrument', instrument)
+block.set_pair('_exptl_adsorptive', adsorptive)
+block.set_pair('_exptl_temperature', temperature)
+block.set_pair('_exptl_sample_mass', str(sample_mass))
+block.set_pair('_sample_id', sample_id)
+block.set_pair('_sample_material_id', material_id)
 
-block["_adsorp_pressure"] = ads_press
-block["_adsorp_p0"] = ads_p0
-block["_adsorp_amount"] = ads_vol
+#write adsorption data
+loop_ads = block.init_loop('_adsorp_', ['pressure','p0', 'amount'])
+loop_ads.set_all_values([list(ads_press.astype(str)), list(ads_p0.astype(str)), list(ads_vol.astype(str))])
 
-loops.append(["_adsorp_pressure","_adsorp_p0", "_adsorp_amount"])
+#write desorption data
+loop_des = block.init_loop('_desorp_', ['pressure','p0', 'amount'])
+loop_des.set_all_values([list(des_press.astype(str)), list(des_p0.astype(str)), list(des_vol.astype(str))])
 
-
-block["_desorp_pressure"] = des_press
-block["_desorp_p0"] = des_p0
-block["_desorp_amount"] = des_vol
-
-loops.append(["_desorp_pressure","_desorp_p0", "_desorp_amount"])
-
-d = OrderedDict()
-header = "raw2ciftest"
[…]

### 2020-11-30 manuscript/article.tex
first draft somewhat complete

@@
 These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
-Subsequently an AIF is produced using the pymatgen CIF routines.\cite{10.1016/j.commatsci.2012.10.028}
-This demonstrated that routines and methods developed for treating CIF files can be used in this application to adsorption data.
-Furthermore, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
+Subsequently an AIF is produced using \textit{gemmi} CIF routines.\cite{gemmi}
+As a consequence routines and methods developed for treating CIF files can be used in this application to adsorption data.
+For example produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
 We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
@@
 \section{Summary and perspective}
-The rise in interest of new advanced adsorbents for application in promising areas has followed a lack of detailed and open reporting of experimental or even computational studies.
-This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
-The AIF is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
-This format represents the first steps to an open adsorption data format.
-An open format sorely needed for the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials.
+There is a current need to a universal format for archiving adsorption data.
+This is pertinent for the development of detailed databases of information that can play an important role in further materials design.\cite{10.1021/acs.chemmater.9b03376}
+This report details the specification of a new standard file, named AIF, based on the self-defining text archive and retrieval (STAR) procedure, inspired by similar universal and evolving formats currently used in the larger scientific community.
+The AIF is importantly an easily extended free-format archive file that can be both human and machine readable.
+This format represents the first steps to an open adsorption data format and the community is encouraged to take up this format.
 

### 2020-11-30 manuscript/article.tex
shared with coauthors

@@
 
-\linenumbers
+% \linenumbers
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 As a consequence routines and methods developed for treating CIF files can be used in this application to adsorption data.
-For example produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the the fastest open-source CIF parser.\cite{gemmi}
+For example produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the fastest open-source CIF parser.\cite{gemmi}
 We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
@@
 DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
-The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~/ref{fgr:example}).
+The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~\ref{fgr:example}a).
 From this plot the isotherm can be classified  as  type  Ib, clearly exhibiting characteristics of a hierarchal pore system with micropores and mesopores.

### 2020-12-16 manuscript/article.tex
GUI working

@@
 \begin{abstract}
-  The rise in interest of new advanced adsorbents for application in promising areas has followed a lack of detailed and open reporting of experimental or even computational studies.
-  This report details the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
+  New advanced adsorbents are a crucial driver for the development of energy and environmental applications.
+  A tremendous potential is nowadays provided by machine learning and data mining techniques to identify an adsorbent for a particular application.
+  However, the current scientific reporting of adsorption isotherms in graphs and figures is not adequate to reproduce original experimentally measured data. 
+  This report proposes the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
   The AIF  is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
-  This format represents the first steps to an open adsorption data format.
-  An open format sorely needed for the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials.
+  This format represents the first steps toward an open adsorption data format as a basis for a decentralized adsorption data library.
+  Such an open format may facilitate the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials in future.
 \end{abstract}

### 2020-12-16 raw2aif_gui.py

@@ -1,0 +1,313 @@
+import numpy as np
+import sys
+from dateutil.parser import parse
+import re
+
+import tkinter as tk
+from tkinter import Tk, filedialog, Button, Label, mainloop, Radiobutton, Entry
+
+# load tkinter
+root = Tk()
+
+# define a browse file function
+def browsefunc():
+    global filename
+    filename = filedialog.askopenfilename()
+    pathlabel.config(text=filename)
+
+# for debuging
+# def writetofile():
+#     print(filename)
+#     print(var.get())
+#     print(matID.get())
+#     outputfilename = filename+".aif"
+#     print(outputfilename)
+
+#covert txt files to aif
+def convertAIF():
+    filetype = var.get()
+    material_id = matID.get()
+
+    if filetype == "quantachrome":
+
+        #load datafile
+        with open(filename, "r", encoding="ISO-8859-1") as fp:
+            lines = fp.readlines()
+
+        # get experimental and material parameters
+
+        for index,line in enumerate(lines):
+            if "Operator" in line:
+                operator = line.split()[1]
+                if operator.split(":")[0] == "Date":
+                    operator = ' '
+            if "Date" in line:
+                date = []
+                for index,element in enumerate(line.split()):
+                    if element.startswith('Date'):
+                        date.append(line.split()[index])
+                date = date[0]
+                date = parse(date.split(':')[-1])
+            if "Instrument" in line:
+                for index,element in enumerate(line.split()):
+                    if element == "Instrument:":
+                        instrument = line.split()[index+1]
+            if "Analysis gas" in line:
+                adsorptive = line.split()[2]
+            if "Bath temp." in line:
+                temperature = line.split()[-2]
+            if "Sample Weight" in line:
+                for index,element in enumerate(line.split()):
+                    if element == "Weight:":
+                        sample_mass = float(line.split()[index+1])
+            if "Sample ID:" in line:
+                sample_id = line.split()[2]
+                sample_id = sample_id.split("Filename")[0]
+
+            if "Press" in line:
+                ads_start = (index+4)
+            
+        # get the adsorption data
+
+        raw_press = []
+        raw_p0 = []
+        raw_vol = []
[…]

### 2020-12-16 raw2aif_gui.py
include a pop-up when aif file is created

@@ -1,13 +1,13 @@
 import numpy as np
-import sys
 from dateutil.parser import parse
 import re
 
 import tkinter as tk
-from tkinter import Tk, filedialog, Button, Label, mainloop, Radiobutton, Entry
+from tkinter import Tk, filedialog, Button, Label, mainloop, Radiobutton, Entry, Toplevel
 
 # load tkinter
 root = Tk()
+root.title('raw2aif')
 
 # define a browse file function
 def browsefunc():
@@ -15,13 +15,14 @@ def browsefunc():
     filename = filedialog.askopenfilename()
     pathlabel.config(text=filename)
 
-# for debuging
+# # for debuging
 # def writetofile():
 #     print(filename)
 #     print(var.get())
 #     print(matID.get())
 #     outputfilename = filename+".aif"
 #     print(outputfilename)
+
 
 #covert txt files to aif
 def convertAIF():
@@ -284,6 +285,13 @@ def convertAIF():
     outputfilename = filename+".aif"
     d.write_file(outputfilename)
 
+    #tkinter popup 
+    toplevel = Toplevel()
+    popupmessage = "AIF file created"
+    label = Label(toplevel, text=popupmessage, height=0, width=100)
+    label.pack()
+    toplevel.focus_force() 
+
 
 # gui details
 
@@ -295,11 +303,11 @@ pathlabel.pack()
 
 
 var = tk.StringVar()
-r1 = tk.Radiobutton(root, text='Quantachrome', variable=var, value='quantachrome')
+r1 = tk.Radiobutton(root, text='Quantachrome (.txt)', variable=var, value='quantachrome')
 r1.pack()
-r2 = tk.Radiobutton(root, text='BELSORP-max', variable=var, value='BELSORP-max')
+r2 = tk.Radiobutton(root, text='BELSORP-max (.dat)', variable=var, value='BELSORP-max')
 r2.pack()
-r3 = tk.Radiobutton(root, text='BELSORP-max-csv', variable=var, value='BELSORP-max-csv')
+r3 = tk.Radiobutton(root, text='BELSORP-max-csv (.csv)', variable=var, value='BELSORP-max-csv')
 r3.pack()
 
 matID = tk.StringVar()

### 2020-12-16 raw2aif.py
Fix style

@@ -1,7 +1,9 @@
-import numpy as np
-import sys
 from dateutil.parser import parse
 import re
+import sys
+
+from gemmi import cif
+import numpy as np
 
 filename = sys.argv[1]
 filetype = sys.argv[2]
@@ -9,26 +11,26 @@ material_id = sys.argv[3]
 
 if filetype == "quantachrome":
 
-    #load datafile
+    # load datafile
     with open(filename, "r", encoding="ISO-8859-1") as fp:
         lines = fp.readlines()
 
     # get experimental and material parameters
 
-    for index,line in enumerate(lines):
+    for index, line in enumerate(lines):
         if "Operator" in line:
             operator = line.split()[1]
             if operator.split(":")[0] == "Date":
                 operator = ' '
         if "Date" in line:
             date = []
-            for index,element in enumerate(line.split()):
+            for index, element in enumerate(line.split()):
                 if element.startswith('Date'):
                     date.append(line.split()[index])
             date = date[0]
             date = parse(date.split(':')[-1])
         if "Instrument" in line:
-            for index,element in enumerate(line.split()):
+            for index, element in enumerate(line.split()):
                 if element == "Instrument:":
                     instrument = line.split()[index+1]
         if "Analysis gas" in line:
@@ -36,7 +38,7 @@ if filetype == "quantachrome":
         if "Bath temp." in line:
             temperature = line.split()[-2]
         if "Sample Weight" in line:
-            for index,element in enumerate(line.split()):
+            for index, element in enumerate(line.split()):
                 if element == "Weight:":
                     sample_mass = float(line.split()[index+1])
         if "Sample ID:" in line:
@@ -45,13 +47,13 @@ if filetype == "quantachrome":
 
         if "Press" in line:
             ads_start = (index+4)
-        
+
     # get the adsorption data
 
     raw_press = []
     raw_p0 = []
     raw_vol = []
-    for index,line in enumerate(lines):
+    for index, line in enumerate(lines):
         if index >= ads_start:
             raw_press.append(float(line.split()[0]))
             raw_p0.append(float(line.split()[1]))
@@ -60,7 +62,7 @@ if filetype == "quantachrome":
 
[…]

### 2020-12-16 read_isotherm_belsorp.py

@@ -8,14 +8,14 @@ material_id = "DUT-67"
 
 if filetype == "BELSORP-max":
 
-    #load datafile
+    # load datafile
     with open(filename, "r", encoding="ISO-8859-1") as fp:
         lines = fp.readlines()
 
 
     # get experimental and material parameters
 
-    for index,line in enumerate(lines):
+    for index, line in enumerate(lines):
         if "Comment2" in line:
             operator = line.split()[1][1:-1]
         if "Date of measurement" in line:
@@ -38,13 +38,13 @@ if filetype == "BELSORP-max":
             ads_start = (index+3)
         if "Desorption data" in line:
             des_start = (index+3)
-        
+
     # # get the adsorption data
 
     raw_press = []
     raw_p0 = []
     raw_vol = []
-    for index,line in enumerate(lines):
+    for index, line in enumerate(lines):
         try:
             if int(line.split()[0]) > 0:
                 if index >= ads_start:
@@ -61,7 +61,7 @@ if filetype == "BELSORP-max":
 
     # change units to standard units
 
-    #pressure from kPa to Pa
+    # pressure from kPa to Pa
     raw_press = np.array(raw_press)*1000
     raw_p0 = np.array(raw_p0)*1000
 
@@ -106,20 +106,19 @@ if filetype == "BELSORP-max":
     block["_adsorption_p0"] = ads_p0
     block["_adsorption_amount"] = ads_vol
 
-    loops.append(["_adsorption_pressure","_adsorption_p0", "_adsorption_amount"])
+    loops.append(["_adsorption_pressure", "_adsorption_p0", "_adsorption_amount"])
 
 
     block["_desorption_pressure"] = des_press
     block["_desorption_p0"] = des_p0
     block["_desorption_amount"] = des_vol
 
-    loops.append(["_desorption_pressure","_desorption_p0", "_desorption_amount"])
+    loops.append(["_desorption_pressure", "_desorption_p0", "_desorption_amount"])
 
     d = OrderedDict()
     header = "raw2ciftest"
-    d[header] = CifBlock(block, loops,header)
+    d[header] = CifBlock(block, loops, header)
     out = CifFile(d)
 
     with zopen(str(sample_id)+'.aif', "wt") as f:
         f.write(out.__str__())
-

### 2020-12-16 manuscript/article.tex
revisions c/o Kaskel

@@
   New advanced adsorbents are a crucial driver for the development of energy and environmental applications.
-  A tremendous potential is nowadays provided by machine learning and data mining techniques to identify an adsorbent for a particular application.
+  Tremendous potential is provided by machine learning and data mining techniques able to identify an adsorbent for a particular application.
   However, the current scientific reporting of adsorption isotherms in graphs and figures is not adequate to reproduce original experimentally measured data.
@@
   This format represents the first steps toward an open adsorption data format as a basis for a decentralized adsorption data library.
-  Such an open format may facilitate the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials in future.
+  An open format is key to facilitate the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials for the future.
 \end{abstract}
@@
 Unfortunately, the existing ecosystem surrounding scholarly data publication often prevents the research community extracting maximum benefit from published reports.
-This led to the foundational principles as discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
+This led to the foundational principles as discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
 
@@
 To facilitate the comparison of adsorption data, the IUPAC also recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$ plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the experiment temperature, or when the temperature is above the critical temperature of the adsorbing gas, against absolute pressure.
+However, in particular for microporous materials, this documentation leads to severe loss of information, as the pore filling occurs at a characteristic $p/p_0$ \textless\textless 0.01 that is not retractable from the isotherm plot.
+Only a logarithmic plot can reveal the characteristic$ p/p_0$ of pore filling, which is an important information to estimate pore size distributions in the micropore regime.
+Similar aspects are also relevant for other branches/regions of the isotherm.
 
-Rapid advances in computer simulations, coupled with the expansion of fruitful local, national and international networks, have fueled the need for a standardization of adsorption data beyond the current IUPAC recommendations.
+Rapid advances in computer simulations, and the quest for developing a digital data space for data mining through national and international networks,have fueled the need for a standardization of adsorption data beyond the current IUPAC recommendations.
 The variety and relative inflexibility of existing adsorption data formats and conventional graphical reporting inhibits the effective use of reported data.
+In particular, a comparison of experimental and computational data is obscured due to the poor documentation of explicit numbers.
 A general, flexible, rapidly extensible and universal file format protocol following the guidelines presented by Wilkinson et al.
-is essential to further accelerate the development of porous materials.
-As with other standard formats, this must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
+will boost the development of porous materials and reveal their application potential.
+Moreover, it enables to validate and advance theoretical methods as a wider and more precise database is openly accessible to validate, for example force field parameters, interactions potentials, isotherm models and more.
+As with other standard formats, such a format must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
 It must also allow new data items to be incorporated without the need to modify existing files to enable an evolving format.
@@
 The data stored in a STAR file is self-descriptive as the underpinning data structure consists of tag-value pairs or data item.
-This data item is the combination a data value with the data name, an identifying unique tag.
+This data item is the combination of a data value with a data name, an identifying unique tag.
 This approach is flexible and able to represent.
@@
 
-For each data point measured during an adsorption experiments data can be stored that relates to the equilibrated pressure, the saturation pressure and the amount adsorbed.
+For each data point measured during an adsorption experiment data can be stored that relates to the equilibrated pressure, the saturation pressure and the amount adsorbed.
 Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.\cite{10.1515/pac-2014-1117}
@@
 As a result, it describes only basic information that usually exported from adsorption instruments and a few convenient metadata items.
-The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements, or combined with CIF data names to archive in situ measurements.
+The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements, or combined with CIF data names for crystalline materials to archive parallelized adsorption-diffraction measurements.
 
 \section{Creating and using the AIF}
-A simple python 3.7 routine was produced during the development of the AIF to convert the plain text data output from Quantachrome and Belsorb instruments, used in our lab and many others.
+A simple python 3.8 routine was prepared during the development of the AIF to convert the plain text data output from Quantachrome (now Anton Paar) and Belsorb (Microtrac) instruments, used in many laboratories around the world.
 Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (\textit{.DAT}) and CSV files exported by Belsorb software.
-At this moment we are unable to read binary data files that are saved by Quatachrome instruments (\textit{.qps}).
+Instrument manufacturers are encouraged to provide readable raw data files in future.
+For example, it is currently not possible to read binary data files e.g. the files saved by Quatachrome instruments (\textit{.qps}).
+Our routine is easily transferable and will be adapted for other instruments in future.
+The source code is provided on GitHub (\ref{www.github.com/jackevansadl/jubilant-waddle}{www.github.com/jackevansadl/jubilant-waddle}) and can be adapted individually by instrument manufacturers.
 
@@
 As a consequence routines and methods developed for treating CIF files can be used in this application to adsorption data.
-For example produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the fastest open-source CIF parser.\cite{gemmi}
+For example, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the fastest open-source CIF parser.\cite{gemmi}
 We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
@@
 To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
-The porous material DUT-6 (also referred to as MOF-206) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
+The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
 DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
@@
 There is evidently a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
-The low pressure regions is important for understanding the process of initial pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
+The low pressure regions is important for understanding the process of sequential pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
 The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
@@
 \section{Summary and perspective}
-There is a current need to a universal format for archiving adsorption data.
-This is pertinent for the development of detailed databases of information that can play an important role in further materials design.\cite{10.1021/acs.chemmater.9b03376}
+There is a current need to develop a universal format for archiving adsorption data.
+This is pertinent for the development of detailed databases of information that can play an important role in further materials design, application data mining, and for developing machine learning computational methods for adsorption processes.
+\cite{10.1021/acs.chemmater.9b03376}
 This report details the specification of a new standard file, named AIF, based on the self-defining text archive and retrieval (STAR) procedure, inspired by similar universal and evolving formats currently used in the larger scientific community.
@@
 acknowledges the support of the Alexander von Humboldt foundation and HPC platforms provided by a GENCI grant (A0070807069) and the Center for Information Services and High Performance Computing (ZIH) at TU Dresden.
+  We thank 
 \end{acknowledgement}

### 2020-12-18 manuscript/article.tex
revision c/o Bon

@@
 This has led to many exciting applications for porous materials, including ion exchange, gas storage, separations and catalysis.\cite{10.1039/C6CS00135A}
-Measuring the interaction of gas with a material is crucial to understanding and comparing different porous materials.
+Measuring the interaction of fluid with a material is crucial to understanding and comparing different porous materials and is usually quantified in the form of an isotherm, which represents the adsorbed amount at equilibrium pressure at a constant temperature.
 The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{10.1515/pac-2014-1117}
-To facilitate the comparison of adsorption data, the IUPAC also recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$ plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the experiment temperature, or when the temperature is above the critical temperature of the adsorbing gas, against absolute pressure.
+To facilitate the comparison of adsorption data, the IUPAC also recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$ plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation vapor pressure of the pure adsorptive at the experiment temperature, or when the temperature is above the critical temperature of the adsorbing gas, against absolute pressure.
 However, in particular for microporous materials, this documentation leads to severe loss of information, as the pore filling occurs at a characteristic $p/p_0$ \textless\textless 0.01 that is not retractable from the isotherm plot.
@@
 This data item is the combination of a data value with a data name, an identifying unique tag.
-This approach is flexible and able to represent.
-nested and repetitive data, which are particularly important for the collection of pressure and adsorbed amount that comprise an adsorption isotherm experiment.
+This approach is flexible and able to represent nested and repetitive data, which are particularly important for the collection of pressure and adsorbed amount that comprise an adsorption isotherm experiment.
 
@@
 It starts with a data block code statement (\texttt{data\_example}) where a block code is a unique identifying code with in a file.
-A data block is closed by another either another data block code statement or the end of file.
+A data block is closed by either another data block code statement or the end of file.
 Comment lines can be placed anywhere in the file and are identified by a hash (\texttt{\#}) symbol.
@@
 Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.\cite{10.1515/pac-2014-1117}
-The saturation pressure can be recorded at each data point as we have discovered that some instruments will calculate and report this value for every point.
+The saturation pressure can be recorded at each data point as we have discovered that some instruments will meausure and report this value for every point.
 
@@
 As a result, it describes only basic information that usually exported from adsorption instruments and a few convenient metadata items.
-The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements, or combined with CIF data names for crystalline materials to archive parallelized adsorption-diffraction measurements.
+The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements and leak checks, or combined with CIF data names for crystalline materials to archive parallelized adsorption-diffraction measurements.
 
 \section{Creating and using the AIF}
-A simple python 3.8 routine was prepared during the development of the AIF to convert the plain text data output from Quantachrome (now Anton Paar) and Belsorb (Microtrac) instruments, used in many laboratories around the world.
+A simple python 3.8 routine was prepared during the development of the AIF to convert the plain text data output from 3P instruments (formerly Quantachrome) and Microtrac Retsch (formerly BEL Japan and BEL Europe) instruments, used in many laboratories around the world.
 Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (\textit{.DAT}) and CSV files exported by Belsorb software.
 Instrument manufacturers are encouraged to provide readable raw data files in future.
-For example, it is currently not possible to read binary data files e.g. the files saved by Quatachrome instruments (\textit{.qps}).
+For example, it is currently not possible to read binary data files e.g. the files saved by 3P instruments (\textit{.qps}).
 Our routine is easily transferable and will be adapted for other instruments in future.
 The source code is provided on GitHub (\ref{www.github.com/jackevansadl/jubilant-waddle}{www.github.com/jackevansadl/jubilant-waddle}) and can be adapted individually by instrument manufacturers.
+In future, we also plan to include as routine for the transformation of files produced by Micromeritics instruments.
 
@@
 The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
-DUT-6 has mesopores with dodecahedral geometry and smaller cages that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
+DUT-6 has mesopores of 2.4~nm, with dodecahedral geometry, and smaller cages of 0.9~nm that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
 The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~\ref{fgr:example}a).

### 2020-12-18 manuscript/article.tex
revisions c/o Senkovska

@@
 \usepackage{booktabs}
+\usepackage{hyperref}
 
@@
 \affiliation[TU Dresden]
-{Department of inorganic chemistry
-Technische Universität Dresden
+{Department of Inorganic Chemistry,
+Technische Universität Dresden,
 Bergstraße 66, 01062 Dresden, Germany}
@@
 This has led to many exciting applications for porous materials, including ion exchange, gas storage, separations and catalysis.\cite{10.1039/C6CS00135A}
-Measuring the interaction of fluid with a material is crucial to understanding and comparing different porous materials and is usually quantified in the form of an isotherm, which represents the adsorbed amount at equilibrium pressure at a constant temperature.
+Measuring the interaction of fluid with a material is crucial to understanding and comparing different porous materials and this is usually quantified in the form of an isotherm, which represents the adsorbed amount at equilibrium pressure at a constant temperature.
 The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{10.1515/pac-2014-1117}
@@
 The currently accepted AIF data names are listed and defined in Table~\ref{tbl:example}.
-These data items form a first version of a core dictionary, which are intended for primarily reporting primary physisorption data for gas on porous materials.
+These data items form a first version of a core dictionary, which are intended for primarily reporting primary physisorption data.
 As a result the dictionary contains information about crucial experimental parameters, basic sample characterization, adsorption and desorption measures, each distinguished by a data name prefix (\texttt{\_exptl\_}, \texttt{\_sample\_}, \texttt{\_adsorp\_} and \texttt{\_desorp\_}).
@@
 \begin{table}
+  \renewcommand{\arraystretch}{1.5}
   \caption{Core dictionary of data items}
   \label{tbl:example}
-  \begin{tabular}{@{}ll@{}}
+  \begin{tabular}{lp{7cm}}
     \toprule
@@
     \texttt{\_sample\_material\_name}  & designated name for the material (string) \\
-    \texttt{\_adsorp\_pressure} & pressure of the adsorption measurement (float, pascal)\\
-    \texttt{\_adsorp\_p0} & saturation pressure of the adsorption measurement (float, pascal) \\
+    \texttt{\_adsorp\_pressure} & equilibrium pressure of the adsorption measurement (float, pascal)\\
+    \texttt{\_adsorp\_p0} & saturation pressure of the adsorption measurement at the temperature of the experiment (float, pascal) \\
     \texttt{\_adsorp\_amount} & amount adsorbed during the adsorption measurement (float, mol$\,$kg$^{-1}$) \\
-    \texttt{\_desorp\_pressure} & pressure of the desorption measurement (float, pascal) \\
-    \texttt{\_desorp\_p0} & saturation pressure of the desorption measurement (float, pascal) \\
+    \texttt{\_desorp\_pressure} & equilibrium  pressure of the desorption measurement (float, pascal) \\
+    \texttt{\_desorp\_p0} & saturation pressure of the desorption measurement at the temperature of the experiment (float, pascal) \\
     \texttt{\_desorp\_amount} & amount adsorbed during the desorption measurement (float, mol$\,$kg$^{-1}$) \\
@@
 
-For each data point measured during an adsorption experiment data can be stored that relates to the equilibrated pressure, the saturation pressure and the amount adsorbed.
+For each data point measured during an adsorption experiment data can be stored that relates to the equilibrium pressure, the saturation pressure and the amount adsorbed.
 Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.\cite{10.1515/pac-2014-1117}
@@
 As a result, it describes only basic information that usually exported from adsorption instruments and a few convenient metadata items.
-The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements and leak checks, or combined with CIF data names for crystalline materials to archive parallelized adsorption-diffraction measurements.
+The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements and leak checks, or combined with CIF data names for structural data to archive parallelized adsorption-diffraction measurements.
 
@@
 Our routine is easily transferable and will be adapted for other instruments in future.
-The source code is provided on GitHub (\ref{www.github.com/jackevansadl/jubilant-waddle}{www.github.com/jackevansadl/jubilant-waddle}) and can be adapted individually by instrument manufacturers.
+The source code is provided on GitHub (\url{www.github.com/jackevansadl/jubilant-waddle}) and can be adapted individually by instrument manufacturers.
 In future, we also plan to include as routine for the transformation of files produced by Micromeritics instruments.
@@
 Subsequently an AIF is produced using \textit{gemmi} CIF routines.\cite{gemmi}
-As a consequence routines and methods developed for treating CIF files can be used in this application to adsorption data.
+As a consequence routines and methods developed for treating CIF files can be used in this application to physisorption data.
 For example, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the fastest open-source CIF parser.\cite{gemmi}
@@
 To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
-The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylic acid and benzene-1,3,5-tribenzoic acid.\cite{10.1002/anie.200904599}
+The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylate and benzene-1,3,5-tribenzoate.\cite{10.1002/anie.200904599}
 DUT-6 has mesopores of 2.4~nm, with dodecahedral geometry, and smaller cages of 0.9~nm that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
@@
 There is a current need to develop a universal format for archiving adsorption data.
-This is pertinent for the development of detailed databases of information that can play an important role in further materials design, application data mining, and for developing machine learning computational methods for adsorption processes.
+This is pertinent for the development of detailed databases of information that can play an important role in future materials design, application data mining, and for developing machine learning computational methods for adsorption processes.
 \cite{10.1021/acs.chemmater.9b03376}

### 2021-01-11 manuscript/article.tex
final changes to manuscript

@@
 
-% \linenumbers
+%\linenumbers
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tocentry}
+% \begin{tocentry}
 
-The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
-permitted for  \emph{Journal of the American Chemical Society}
-graphical table of content entries. The box will not resize if the
-content is too big: instead it will overflow the edge of the box.
+% The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
+% permitted for  \emph{Journal of the American Chemical Society}
+% graphical table of content entries. The box will not resize if the
+% content is too big: instead it will overflow the edge of the box.
 
-\end{tocentry}
+% \end{tocentry}
 
@@
 It is important in many branches of science for there to exist a uniform and flexible method of archiving and exchanging data.
-The data presented in research contributions must be readily accessible and easily verifiable.
+The data presented in research contributions must be readily accessible and easily verifiable.\cite{10.1021/acs.langmuir.9b02963}
 Key to scientific discovery and innovation the use of good data management practices can  provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1002/adts.201900131}
@@
 The variety and relative inflexibility of existing adsorption data formats and conventional graphical reporting inhibits the effective use of reported data.
-In particular, a comparison of experimental and computational data is obscured due to the poor documentation of explicit numbers.
+The largest adsorption database, NIST/ARPA-E Adsorption Database, contains thousands of isotherms laboriously digitized from journal articles.\cite{NIST}
+In particular, a understanding the comparison between experimental and computational data is difficult due to poor experimental documentation.\cite{10.1021/acs.chemmater.7b04287}
 A general, flexible, rapidly extensible and universal file format protocol following the guidelines presented by Wilkinson et al.
@@
 Our routine is easily transferable and will be adapted for other instruments in future.
-The source code is provided on GitHub (\url{www.github.com/jackevansadl/jubilant-waddle}) and can be adapted individually by instrument manufacturers.
+The source code and a stand-alone program is provided on GitHub (\url{www.github.com/jackevansadl/adsorptioninformationfile}) and can be adapted individually by instrument manufacturers.
 In future, we also plan to include as routine for the transformation of files produced by Micromeritics instruments.
@@
 The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylate and benzene-1,3,5-tribenzoate.\cite{10.1002/anie.200904599}
-DUT-6 has mesopores of 2.4~nm, with dodecahedral geometry, and smaller cages of 0.9~nm that produce an extremely porous material with large adsorption capacities for\textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
+DUT-6 has mesopores of 2.4~nm, with dodecahedral geometry, and smaller cages of 0.9~nm that produce an extremely porous material with large adsorption capacities for \textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
 The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~\ref{fgr:example}a).
@@
 
-% \begin{equation}
-%   \Omega\left(N_{\mathrm{host}}, p, \sigma_{a}=\mathbf{0}, T ; V\right)=F_{\mathrm{host}}\left(N_{\mathrm{host}}, T ; V\right)+p V-\int_{-\infty}^{\mu(p, T)} N_{\mathrm{guest}}\left(N_{\mathrm{host}}, \mu^{\prime}, \sigma_{a}=\mathbf{0}, T ; V\right) \mathrm{d} \mu^{\prime}
-%   \label{eqn:osmoticequation}
-% \end{equation}
-
-  % \begin{figure}[htb]
-  %   \includegraphics{../figures/figure2-01.png}
-  %     \caption{}
-  %     \label{fgr:figure2}
-  %   \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 acknowledges the support of the Alexander von Humboldt foundation and HPC platforms provided by a GENCI grant (A0070807069) and the Center for Information Services and High Performance Computing (ZIH) at TU Dresden.
-  We thank 
+  We thank Ren Koh for assistance with the development of the raw2aif file converter and Andrew Tarzia (University College London) for testing the program.
 \end{acknowledgement}

### 2021-01-14 raw2aif.py
date-time fix

@@ -245,7 +245,7 @@ block = d.sole_block()
 
 # write metadata
 block.set_pair('_exptl_operator', operator)
-block.set_pair('_exptl_date', str(date))
+block.set_pair('_exptl_date', str(date.date()))
 block.set_pair('_exptl_instrument', instrument)
 block.set_pair('_exptl_adsorptive', adsorptive)
 block.set_pair('_exptl_temperature', str(temperature))

### 2021-01-14 raw2aif_gui.py

@@ -266,7 +266,7 @@ def convertAIF():
 
     # write metadata
     block.set_pair('_exptl_operator', operator)
-    block.set_pair('_exptl_date', str(date))
+    block.set_pair('_exptl_date', str(date.date()))
     block.set_pair('_exptl_instrument', instrument)
     block.set_pair('_exptl_adsorptive', adsorptive)
     block.set_pair('_exptl_temperature', str(temperature))

### 2021-01-14 read_isotherm_belmaxcsv.py

@@ -1,117 +1,0 @@
-import numpy as np
-import sys
-from dateutil.parser import parse
-
-filename = 'database/DUT-32/RGE-343-DUT32-7dCO2_Nitrogen (BelMax).csv'
-filetype = "BELSORP-max-csv"
-material_id = "DUT-32"
-
-if filetype == "BELSORP-max-csv":
-
-    #load datafile
-    with open(filename, "r", encoding="ISO-8859-1") as fp:
-        lines = fp.readlines()
-
-
-    # get experimental and material parameters
-
-    for index,line in enumerate(lines):
-        if "COMMENT2" in line:
-            operator = line.split(',')[-1]
-        if "Date of measurement" in line:
-            date = line.split(',')[-1]
-            date = parse(date.split(':')[-1])
-        if "Serial number" in line:
-            instrument = line.split(',')[-1]
-            instrument = "BELSORP-max-"+str(instrument)
-        if "Adsorptive" in line:
-            adsorptive = line.split(',')[-1]
-        if "Adsorption temperature" in line:
-            temperature = float(line.split(',')[1])
-        if "Sample weight" in line:
-            sample_mass = float(line.split(',')[1])
-        if "COMMENT1" in line:
-            sample_id = line.split(',')[-1]
-
-        if "ADS" in line:
-            ads_start = index+1
- 
-    # # get the adsorption data
-
-    raw_press = []
-    raw_p0 = []
-    raw_vol = []
-    for index,line in enumerate(lines):
-        if index >= ads_start:
-            if line.split(',')[0] != "DES\n":
-                if int(line.split(',')[0]) > 0:
-                    if index >= ads_start:
-                        raw_press.append(float(line.split(',')[2]))
-                        raw_p0.append(float(line.split(',')[3]))
-                        raw_vol.append(float(line.split(',')[-1]))
-
-
-    # change units to standard units
-
-    #pressure from kPa to Pa
-    raw_press = np.array(raw_press)*1000
-    raw_p0 = np.array(raw_p0)*1000
-
-    # amount adsorbed from mL/g to mmol/g
-    raw_vol = np.array(raw_vol)/22.414
-
-    print(raw_press)
-
-    # split ads / desorption branches
-
-    turning_point = np.argmax(raw_press)
-
-    ads_press = raw_press[:turning_point+1]
-    des_press = raw_press[turning_point+1:]
[…]

### 2021-01-14 read_isotherm_belsorp.py

@@ -1,124 +1,0 @@
-import numpy as np
-import sys
-from dateutil.parser import parse
-
-filename = 'database/DUT-67/DUT67_1_Garching_acetone_298K.DAT'
-filetype = "BELSORP-max"
-material_id = "DUT-67"
-
-if filetype == "BELSORP-max":
-
-    # load datafile
-    with open(filename, "r", encoding="ISO-8859-1") as fp:
-        lines = fp.readlines()
-
-
-    # get experimental and material parameters
-
-    for index, line in enumerate(lines):
-        if "Comment2" in line:
-            operator = line.split()[1][1:-1]
-        if "Date of measurement" in line:
-            date = line.split()[-1]
-            date = parse(date.split(':')[-1])
-        if "Instrument S/N" in line:
-            instrument = line.split()[-1]
-            instrument = "BELSORP-max-"+str(instrument)
-        if "Adsorptive" in line:
-            adsorptive = line.split()[-1]
-        if "Meas. Temp./K" in line:
-            temperature = float(line.split()[-1])
-        if "Sample weight/g" in line:
-            sample_mass = float(line.split()[-1])
-        if "Comment1" in line:
-            sample_id = line.split()[-1]
-            sample_id = sample_id[1:-1]
-
-        if "Adsorption data" in line:
-            ads_start = (index+3)
-        if "Desorption data" in line:
-            des_start = (index+3)
-
-    # # get the adsorption data
-
-    raw_press = []
-    raw_p0 = []
-    raw_vol = []
-    for index, line in enumerate(lines):
-        try:
-            if int(line.split()[0]) > 0:
-                if index >= ads_start:
-                    raw_press.append(float(line.split()[1]))
-                    raw_p0.append(float(line.split()[2]))
-                    raw_vol.append(float(line.split()[-1]))
-                if index >= des_start:
-                    raw_press.append(float(line.split()[1]))
-                    raw_p0.append(float(line.split()[2]))
-                    raw_vol.append(float(line.split()[-1]))
-        except:
-            pass
-
-
-    # change units to standard units
-
-    # pressure from kPa to Pa
-    raw_press = np.array(raw_press)*1000
-    raw_p0 = np.array(raw_p0)*1000
-
-    # amount adsorbed from mL/g to mmol/g
-    raw_vol = np.array(raw_vol)/22.414
[…]

### 2021-01-14 readaif.py

@@ -2,14 +2,14 @@ from gemmi import cif
 import matplotlib.pyplot as plt
 import numpy as np
 
-aif = cif.read_file('database/DUT-6/nk_DUT-6_LP_N2_114pkt.aif')
+aif = cif.read('database/Ar_test/1.DAT.aif')
 block = aif.sole_block()
 ads_press = np.array(block.find_loop('_adsorp_pressure'), dtype=float)
 ads_amount = np.array(block.find_loop('_adsorp_amount'), dtype=float)
 des_press = np.array(block.find_loop('_desorp_pressure'), dtype=float)
 des_amount = np.array(block.find_loop('_desorp_amount'), dtype=float)
 
-material_id = block.find_pair('_material_id')[-1]
+material_id = block.find_pair('_sample_material_id')[-1]
 print(material_id)
 
 plt.semilogx(ads_press, ads_amount, 'o-')

### 2021-01-14 readaif_getBETarea.py

@@ -1,164 +1,0 @@
-import numpy as np
-from gemmi import cif
-
-aif = cif.read_file('database/DUT-60/ih_DUT-60_183b.aif')
-block = aif.sole_block()
-ads_press = np.array(block.find_loop('_adsorption_pressure'),dtype=float)
-ads_amount = np.array(block.find_loop('_adsorption_amount'),dtype=float)
-des_press = np.array(block.find_loop('_desorption_pressure'),dtype=float)
-des_amount = np.array(block.find_loop('_desorption_amount'),dtype=float)
-
-material_id = block.find_pair('_material_id')[-1]
-material_mass = block.find_pair('_sample_mass')[-1]
-print(material_id)
-
-#convert to mol/g to cm3/g
-ads_amount=ads_amount*0.001
-#ads_amount = ads_amount / 4.5e-3
-# ads_amount = ads_amount*float(material_mass)
-# ads_amount = ads_amount*1e-6
-
-
-#n2 properties
-p0 = 101860.98004799998
-ads_cross = 0.162
-
-pp0=ads_press/p0
-
-roq_consistency = ads_amount*(1-pp0)
-
-import matplotlib.pyplot as plt
-print(np.argmax(roq_consistency))
-plt.plot(roq_consistency, 'o-')
-plt.show()
-
-lo_limit = 0
-hi_limit= np.argmax(roq_consistency)
-
-# plt.plot(pp0[lo_limit:hi_limit],roq_consistency[lo_limit:hi_limit], 'o-')
-# plt.show()
-
-#transform to limits
-
-pp0 =  pp0[lo_limit:hi_limit]
-roq_consistency = roq_consistency[lo_limit:hi_limit]
-BETeq = pp0/roq_consistency
-
-
-
-plt.plot(pp0,BETeq,'o-')
-plt.show()
-
-from scipy.stats import linregress
-
-def rolling_window(a, window):
-    shape = a.shape[:-1] + (a.shape[-1] - window + 1, window)
-    strides = a.strides + (a.strides[-1],)
-    return np.lib.stride_tricks.as_strided(a, shape=shape, strides=strides)
-
-BETeq_window = rolling_window(BETeq,3)
-pp0_window = rolling_window(pp0,3)
-
-
-
-output = []
-for window in range(len(BETeq_window)):
-    c=[]
-    slope=[]
[…]

### 2021-01-14 manuscript/CoverLetter.tex
manuscript finalised

% Cover letter using letter.sty
\documentclass[11pt, a4paper]{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=10in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.8in   % textwidth of 6.5in leaves 1 inch for right margin
\setlength{\footskip}{1in}

\usepackage{sansmathfonts}
\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}
\renewcommand{\rmdefault}{\sfdefault}
\usepackage{fontspec}
\usepackage[final]{pdfpages}

\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{hyperref}
\definecolor{blues}{HTML}{002F5D}
\definecolor{blues2}{HTML}{0068B4}
\definecolor{orange}{HTML}{EF7C00}
%\newcommand*\faMobile{{\FA\symbol{"F10B}}}
\newcommand*\varhrulefill[1][0.4pt]{\leavevmode\leaders\hrule height#1\hfill\kern0pt}

\usepackage{fontspec}
\setmainfont[Ligatures=TeX,BoldFont={Myriad Pro Semibold}]{Myriad Pro}

\renewcommand{\sfdefault}{\rmdefault}

\begin{document}

\signature{Dr Jack D. Evans}           % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{ }
\noindent
\begin{minipage}[t]{.6\textwidth}
~\par\vspace{-\baselineskip}
\includegraphics[height=2cm]{TU_Dresden_Logo_HKS41.eps}
\vfill
\end{minipage}%
\begin{minipage}[t]{.4\textwidth}
{\large\bf Dr Jack D. Evans}\smallskip\\
Department of Inorganic Chemistry \\
Technische Universität Dresden \\
\faMobile~+49~163~3776138 \\
\Letter~jack.evans@tu-dresden.de
\end{minipage}%
\bigskip{\color{blues}\hrule}
\vfill % forces letterhead to top of page

\opening{To whom it may concern,}

Please find enclosed our manuscript entitled:

\smallskip
\begin{center}
\noindent \textbf{A universal standard archive file for adsorption data}

\noindent J. D. Evans, V. Bon, I. Senkovska, S. Kaskel
\end{center}
\smallskip

\noindent which we would like to submit for consideration as an \textit{Article} in \textit{Langmuir}.

In this article, we propose a new standard adsorption information file (AIF) for reporting adsorption isotherms, which builds upon other formats used throughout the literature, such as the crystallographic information file (CIF).
This universal archive file, AIF, is an easily extended free-format archive file, and this represents the first steps toward an open adsorption data format that can be used as a basis for a decentralized adsorption data library.
The use of open formats is a key requirement to facilitate the electronic transmission of adsorption data between laboratories, journals and larger databases in an effort to enhance the reproducibility of science in the field of porous materials.

To accompany this work, we have developed scripts and a computer program to generate an AIF from data in various formats produced by several instruments used by many laboratories around the world. This program and details for using the AIF format are freely available on a GitHub repository (\url{https://github.com/jackevansadl/adsorptioninformationformat}).

We believe this work is a springboard for an important discussion of the future of data reporting for porous materials. Thus, we are confident that this manuscript is appropriate and of interest to the readership of \textit{Langmuir}.

\sloppy{Please note, this article has been deposited at the \textit{ChemRxiv} preprint server with the DOI code: \mbox{\url{10.26434/chemrxiv.13562798}}.}

Thank you for your time and consideration of this manuscript.
\closing{Yours sincerely,}

%\encl{}  				% Enclosures

\vfill

\end{letter}

\end{document}

### 2021-01-14 manuscript/article.tex
manuscript finalised

@@
   New advanced adsorbents are a crucial driver for the development of energy and environmental applications.
-  Tremendous potential is provided by machine learning and data mining techniques able to identify an adsorbent for a particular application.
+  Tremendous potential is provided by machine learning and data mining techniques, as these approaches can identify the most appropriate adsorbent for a particular application.
   However, the current scientific reporting of adsorption isotherms in graphs and figures is not adequate to reproduce original experimentally measured data.
   This report proposes the specification of a new standard adsorption information file (AIF) inspired by the ubiquitous crystallographic information file (CIF) and based on the self-defining text archive and retrieval (STAR) procedure, also used to represent biological nuclear magnetic resonance experiments (NMR-STAR).
-  The AIF  is a flexible, general and easily extended free-format archive file and is readily human and machine readable--- simple to edit using a basic text editor or parse for database curation.
+  The AIF  is a flexible and easily extended free-format archive file that is readily human and machine readable and is simple to edit using a basic text editor or parse for database curation.
   This format represents the first steps toward an open adsorption data format as a basis for a decentralized adsorption data library.
-  An open format is key to facilitate the electronic transmission of adsorption data between laboratories, journals and larger databases in the effort to increase open science in the field of porous materials for the future.
+  An open format facilitates the electronic transmission of adsorption data between laboratories, journals and larger databases, which is key in the effort to increase open science in the field of porous materials in the future.
 \end{abstract}
@@
 \section{Introduction}
-It is important in many branches of science for there to exist a uniform and flexible method of archiving and exchanging data.
+In many branches of science, it is important to establish a uniform and flexible method of archiving and exchanging data.
 The data presented in research contributions must be readily accessible and easily verifiable.\cite{10.1021/acs.langmuir.9b02963}
-Key to scientific discovery and innovation the use of good data management practices can  provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1002/adts.201900131}
-Unfortunately, the existing ecosystem surrounding scholarly data publication often prevents the research community extracting maximum benefit from published reports.
-This led to the foundational principles as discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
+Key to scientific discovery and innovation, the use of good data management practices can provide significant knowledge through the reuse of original data by the community after the data publication process.\cite{10.1002/adts.201900131}
+Unfortunately, the existing ecosystem surrounding scholarly data publication often prevents the research community from extracting maximum benefit from published reports.
+This forms the basis of the foundational principles as discussed by Wilkinson et al.--- Findability, Accessibility, Interoperability, and Reusability--- that serve as a guideline to maximize the added-value gained by digital publishing.\cite{10.1038/sdata.2016.18}
 
@@
 This has led to many exciting applications for porous materials, including ion exchange, gas storage, separations and catalysis.\cite{10.1039/C6CS00135A}
-Measuring the interaction of fluid with a material is crucial to understanding and comparing different porous materials and this is usually quantified in the form of an isotherm, which represents the adsorbed amount at equilibrium pressure at a constant temperature.
+Measuring the interaction of fluid with a material is crucial to the understanding and comparison of different porous materials, usually quantified in the form of an isotherm, which represents the adsorbed amount at equilibrium pressure at a constant temperature.
 The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{10.1515/pac-2014-1117}
 To facilitate the comparison of adsorption data, the IUPAC also recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$ plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation vapor pressure of the pure adsorptive at the experiment temperature, or when the temperature is above the critical temperature of the adsorbing gas, against absolute pressure.
-However, in particular for microporous materials, this documentation leads to severe loss of information, as the pore filling occurs at a characteristic $p/p_0$ \textless\textless 0.01 that is not retractable from the isotherm plot.
-Only a logarithmic plot can reveal the characteristic$ p/p_0$ of pore filling, which is an important information to estimate pore size distributions in the micropore regime.
+However, particularly for microporous materials, this documentation leads to extensive loss of information, as the pore filling occurs at a characteristic $p/p_0$ \textless\textless 0.01 that is not retractable from the isotherm plot.
+Only a logarithmic plot can reveal the characteristic$ p/p_0$ of pore filling, which is important information to estimate pore size distributions in the micropore regime.
 Similar aspects are also relevant for other branches/regions of the isotherm.
 
-Rapid advances in computer simulations, and the quest for developing a digital data space for data mining through national and international networks,have fueled the need for a standardization of adsorption data beyond the current IUPAC recommendations.
+Rapid advances in computer simulations, together with the quest for developing a digital data space for data mining through national and international networks, have fueled the need for the standardization of adsorption data beyond the current IUPAC recommendations.
 The variety and relative inflexibility of existing adsorption data formats and conventional graphical reporting inhibits the effective use of reported data.
-The largest adsorption database, NIST/ARPA-E Adsorption Database, contains thousands of isotherms laboriously digitized from journal articles.\cite{NIST}
-In particular, a understanding the comparison between experimental and computational data is difficult due to poor experimental documentation.\cite{10.1021/acs.chemmater.7b04287}
+The largest adsorption database, NIST/ARPA-E Adsorption Database, contains thousands of isotherms that have been laboriously digitized from journal articles.\cite{NIST}
+In particular, an understanding of the comparison between experimental and computational data is difficult due to poor experimental documentation.\cite{10.1021/acs.chemmater.7b04287}
 A general, flexible, rapidly extensible and universal file format protocol following the guidelines presented by Wilkinson et al.
@@
 
-In this submission we outline our proposal for a new standard adsorption information file (AIF) and the clear advantages of this format compared to the currently accepted graphical deposition method.
-The AIF is free-format archive file that is readily human and machine readable, both simple to edit using a basic text editor or parse using computer programs.
+In this submission, we outline our proposal for a new standard adsorption information file (AIF) and the clear advantages of this format compared to the currently accepted graphical deposition method.
+The AIF is a free-format archive file that is readily human and machine readable, both simple to edit using a basic text editor or parse using computer programs.
 This represents the first flexible, general and easily extended format for representing the results of adsorption experiments and the first steps towards standardizing a format for archiving adsorption data.
@@
 \section{AIF structure and syntax}
-The information contained within an AIF is arranged in a strict structural arrangement.
-Alternative data storage structures were considered, during the development the AIF,  such as the comma-separated-value (CSV) file.
+The information contained within an AIF is presented in a strict structural arrangement.
+Alternative data storage structures were considered during the development the AIF, such as the comma-separated-value (CSV) file.
 The key, however, is that a universal data format must also include a well-structured record of metadata associated with the adsorption experiment.
-Without the metadata of, containing at the very least, what gas or temperature was used during the experiment the resulting adsorption data is meaningless.
+Without the metadata containing, at the very least, what gas or temperature was used during the experiment, the resulting adsorption data is meaningless.
 Metadata is also important in the development of databases.
 This is crucial to identify identical or related data, understand the evolution of databases over time, and also permit further examination for specific data items.
-As a result the STAR data structure was adopted,\cite{10.1021/ci00019a005} which is famously used in the crystallographic information file (CIF) and biological nuclear magnetic resonance experiments (NMR-STAR).\cite{10.1107/S010876739101067X,10.1007/s10858-018-0220-3}
+As a result, the STAR data structure was adopted,\cite{10.1021/ci00019a005} which is famously used in crystallographic information file (CIF) and biological nuclear magnetic resonance experiments (NMR-STAR).\cite{10.1107/S010876739101067X,10.1007/s10858-018-0220-3}
 An important property of the STAR format is that its syntax is defined by a few simple rules using an object/relational model.
 The data stored in a STAR file is self-descriptive as the underpinning data structure consists of tag-value pairs or data item.
-This data item is the combination of a data value with a data name, an identifying unique tag.
-This approach is flexible and able to represent nested and repetitive data, which are particularly important for the collection of pressure and adsorbed amount that comprise an adsorption isotherm experiment.
+This data item is the combination of a data value with a data name, identified by a unique tag.
+This approach is flexible and is able to represent nested and repetitive data, which are particularly important for the collection of pressure and adsorbed amount data that comprise an adsorption isotherm experiment.
 
-The data structure of an AIF is comprised of comment lines and data blocks, which contains the required metadata and quantities related to the adsorption experiment, separated for adsorption and desorption (Figure~\ref{fgr:datastructure}).
+The data structure of an AIF is comprised of comment lines and data blocks, which contain the required metadata and quantities related to the adsorption experiment, separated for adsorption and desorption (Figure~\ref{fgr:datastructure}).
 Files can contain any number of data blocks to represent multiple experiments.
-Fundamentally, a data block is a data cell containing a sequence of data items, data loops.
-It starts with a data block code statement (\texttt{data\_example}) where a block code is a unique identifying code with in a file.
+Fundamentally, a data block is a data cell containing a sequence of data items, known as data loops.
+It starts with a data block code statement (\texttt{data\_example}) where a block code is a unique identifying code in a file.
 A data block is closed by either another data block code statement or the end of file.
@@
 Single values or strings can be included within a data block using the data name and data value pairs.
-Data values are preceded by an identifying data name that is identify by an underscore character, for example \texttt{\_temperature}.
-A data loop structure consists of a loop statement (\texttt{loop\_}) followed by a list of data names and then a list of data, each of which contains data values that matches the data names in the list of data names.
-Though data loops can be nested at any level this is not necessary for the current implementation.
+Data values are preceded by an identifying data name that is identified by an underscore character, for example \texttt{\_temperature}.
+A data loop structure consists of a loop statement (\texttt{loop\_}) followed by a list of data names and then a list of data, each of which contains data values that match the data names in the list of data names.
+Although data loops can be nested at any level, this is not necessary for the current implementation.
 Importantly, data values that follow the nested data declarations must be in exact multiples of the number of data names (which are referred to as loop packets).
 The data loops, as used here, are terminated by a new data item, a new data loop or an end of file.
-These data loops can thus straightforwardly represent the data recorded at each point of an adsorption and desorption experiment, for example the pressure and quantities adsorbed.
+Thus, these data loops can straightforwardly represent the data recorded at each point of an adsorption and desorption experiment, for example, the pressure and quantities adsorbed.
 
@@
 An entire experiment can be described within a single data block.
-Initially, data name and data value pairs can be used to identify quantities relating to the whole experiment such as the date and time, temperature and adsorptive.
+Initially, data name and data value pairs can be used to identify quantities relating to the whole experiment, such as the date and time, temperature and adsorptive.
 The data points for the adsorption and desorption branch can then be detailed in separate data loops.
@@
 The currently accepted AIF data names are listed and defined in Table~\ref{tbl:example}.
-These data items form a first version of a core dictionary, which are intended for primarily reporting primary physisorption data.
-As a result the dictionary contains information about crucial experimental parameters, basic sample characterization, adsorption and desorption measures, each distinguished by a data name prefix (\texttt{\_exptl\_}, \texttt{\_sample\_}, \texttt{\_adsorp\_} and \texttt{\_desorp\_}).
+These data items form a first version of a core dictionary, which are primarily intended for reporting primary physisorption data.
+As a result, the dictionary contains information about crucial experimental parameters, basic sample characterization and adsorption and desorption measures, each distinguished by a data name prefix (\texttt{\_exptl\_}, \texttt{\_sample\_}, \texttt{\_adsorp\_} and \texttt{\_desorp\_}).
 
@@
     \texttt{\_exptl\_operator}  & name of the person who ran the experiment (string)  \\
-    \texttt{\_exptl\_date} & date and time of the experiment (date-time string representation) \\
+    \texttt{\_exptl\_date} & date and time of the experiment (YYYY-MM-DD) \\
     \texttt{\_exptl\_instrument}  & instrument id used for the experiment (string)  \\
@@
 
-The goal of the experimental data names is to capture the information required to accurately portray the results of experiment, which at the very minimum are the temperature and adsorptive.
-As metadata should include information that may aid in identifying possible errors this also includes the mass of sample used in the experiment.
-Additionally, data is included relative to the date, time and person responsible for the measurement to produce a general picture of the provenance of the experiment.
+The goal of the experimental data names is to capture the information required to accurately portray the results of an experiment, which at the very minimum are the temperature and adsorptive.
+As the metadata should include information that may aid in identifying possible errors, this also includes the mass of sample used in the experiment.
+Additionally, the data also includes the date and person responsible for the measurement to produce a general picture of the provenance of the experiment.
 
@@
 
-For each data point measured during an adsorption experiment data can be stored that relates to the equilibrium pressure, the saturation pressure and the amount adsorbed.
+For each data point measured during an adsorption experiment, data related to the equilibrium pressure, saturation pressure and amount adsorbed can be stored.
 Importantly, these should be stored in units of pascal and mol$\,$kg$^{-1}$ to follow the IUPAC recommendations.\cite{10.1515/pac-2014-1117}
-The saturation pressure can be recorded at each data point as we have discovered that some instruments will meausure and report this value for every point.
+The saturation pressure can be recorded for each data point, as we have discovered that some instruments will  report this value for every point.
 
-The above features serve as an example of the data that can be archived in a AIF and can be extended in future versions.
-For example, the intention of this initial version is to provide digital archive of the presented primary data of an adsorption experiment, the isotherm.
-As a result, it describes only basic information that usually exported from adsorption instruments and a few convenient metadata items.
-The flexibility of this approach can be extended in future versions to include more detailed parameters not commonly presented, such as dead volume measurements and leak checks, or combined with CIF data names for structural data to archive parallelized adsorption-diffraction measurements.
+The above features serve as an example of the data that can be archived in a AIF, which can be extended in future versions.
+For example, the intention of this initial version is to provide a digital archive of the presented primary data of an adsorption experiment ––– the isotherm.
+As a result, it describes only basic information that is usually exported from adsorption instruments and a few convenient metadata items.
+The flexibility of this approach can be extended in future versions to include more detailed parameters that are not commonly presented, such as dead volume measurements and leak checks, or it could be combined with CIF data names for structural data to archive parallelized adsorption-diffraction measurements.
 
 \section{Creating and using the AIF}
-A simple python 3.8 routine was prepared during the development of the AIF to convert the plain text data output from 3P instruments (formerly Quantachrome) and Microtrac Retsch (formerly BEL Japan and BEL Europe) instruments, used in many laboratories around the world.
+A simple python 3.8 routine was prepared during the development of the AIF to convert the plain text data output from 3P Instruments (formerly Quantachrome) and Microtrac Retsch (formerly BEL Japan and BEL Europe) instruments, used in many laboratories around the world.
 Specifically, this has been written to parse raw analysis text files exported by Quantachrome software and the raw data files (\textit{.DAT}) and CSV files exported by Belsorb software.
-Instrument manufacturers are encouraged to provide readable raw data files in future.
-For example, it is currently not possible to read binary data files e.g. the files saved by 3P instruments (\textit{.qps}).
-Our routine is easily transferable and will be adapted for other instruments in future.
+Instrument manufacturers are encouraged to provide readable raw data files in the future.
+For example, it is currently not possible to read binary data files, for example, the files saved by 3P Instruments (\textit{.qps}).
+Our routine is easily transferable and will be adapted for other instruments in the future.
 The source code and a stand-alone program is provided on GitHub (\url{www.github.com/jackevansadl/adsorptioninformationfile}) and can be adapted individually by instrument manufacturers.
-In future, we also plan to include as routine for the transformation of files produced by Micromeritics instruments.
+In the future, we also plan to include as routine for the transformation of files produced by Micromeritics instruments.
 
@@
 These data items are converted to the appropriate units and the isotherm is split into the adsorption and desorption parts.
-Subsequently an AIF is produced using \textit{gemmi} CIF routines.\cite{gemmi}
-As a consequence routines and methods developed for treating CIF files can be used in this application to physisorption data.
-For example, produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library that is considered the fastest open-source CIF parser.\cite{gemmi}
+Subsequently, an AIF is produced using \textit{gemmi} CIF routines.\cite{gemmi}
+As a consequence, routines and methods developed for treating CIF files can be used in this application to physisorption data.
+For example, the produced AIF files can also be read using existing CIF methods, such as the \texttt{gemmi} python library, considered the fastest open-source CIF parser.\cite{gemmi}
 We have used \texttt{gemmi} library to demonstrate how an isotherm can be displayed from an AIF using a few lines.
-This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in to routines to parse the information directly from binary data used by the instruments.
+This is a very simple implementation and it is hoped that future versions, following the cooperation of several manufactures, could result in routines to parse the information directly from binary data used by the instruments.
 
-To illustrate the importance of a universal data format for adsorption data we can compare data contained within an AIF to data digitized from a figure in a manuscript, for the same experiment.
+To illustrate the importance of a universal data format for adsorption data, we can compare data contained within an AIF to data digitized from a figure in a manuscript for the same experiment.
 The porous material DUT-6 (also referred to as MOF-205) is a metal-organic framework produced from zinc nitrate and two different different ligands; 2,6-naphthalenedicarboxylate and benzene-1,3,5-tribenzoate.\cite{10.1002/anie.200904599}
 DUT-6 has mesopores of 2.4~nm, with dodecahedral geometry, and smaller cages of 0.9~nm that produce an extremely porous material with large adsorption capacities for \textit{n}-butane (up to 1.1~g$\,$g$^{-1}$ at 293~K),  methane (230~mg$\,$g$^{-1}$ at 100~bar and 298~K) and hydrogen (60~mg$\,$g$^{-1}$ at 50~bar and 77~K).
-The nitrogen adsorption isotherm at 77~K was reported in the original manuscript using relative pressure and a linear axis (Figure~\ref{fgr:example}a).
-From this plot the isotherm can be classified  as  type  Ib, clearly exhibiting characteristics of a hierarchal pore system with micropores and mesopores.
+In the original manuscript, the nitrogen adsorption isotherm at 77~K was reported using relative pressure and a linear axis (Figure~\ref{fgr:example}a).
+From this plot, the isotherm can be classified  as  type  Ib, clearly exhibiting characteristics of a hierarchal pore system with micropores and mesopores.
 There is evidently a distinct step $p/p_0$ = 0.17, however, from this plot it is not possible to correctly identify low pressure features.
-The low pressure regions is important for understanding the process of sequential pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
+The low pressure regions are important for understanding the process of sequential pore filling or for independent application of analysis methods, such as the Brunauer–Emmett–Teller (BET) method.\cite{10.1016/S0167-2991(07)80008-5}
 The reported isotherm was digitized using WebPlotDigitizer, which uses a time-consuming but powerful point-picking methodology.\cite{webplotdigitizer}
-In this methodology, each point in the graph is identified by clicking on the image area and the point's location in on-screen pixels is then converted to data values, based on an axes calibration.
-The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows important low pressure information, such as the point of initial pore-filling, is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).
+In this methodology, each point in the graph is identified by clicking on the image area , and the location of the point in on-screen pixels is then converted to data values based on an axes calibration.
+The digitized isotherm and the data from the experiment, when plotted on semi-log axes, clearly shows that important low pressure information, such as the point of initial pore-filling, is lost when this information is simply included as a figure in a manuscript (Figure~\ref{fgr:example}).
 
@@
 There is a current need to develop a universal format for archiving adsorption data.
-This is pertinent for the development of detailed databases of information that can play an important role in future materials design, application data mining, and for developing machine learning computational methods for adsorption processes.
-\cite{10.1021/acs.chemmater.9b03376}
-This report details the specification of a new standard file, named AIF, based on the self-defining text archive and retrieval (STAR) procedure, inspired by similar universal and evolving formats currently used in the larger scientific community.
-The AIF is importantly an easily extended free-format archive file that can be both human and machine readable.
-This format represents the first steps to an open adsorption data format and the community is encouraged to take up this format.
+This is pertinent for the development of detailed databases of information that can play an important role in future materials design, data mining, and for developing machine learning computational methods for adsorption processes.\cite{10.1021/acs.chemmater.9b03376}
+This report details the specification of a new standard file, named AIF, based on the self-defining text archive and retrieval (STAR) procedure, inspired by similar universal and evolving formats that are currently used in the larger scientific community.
+Importantly, the AIF is an easily extended free-format archive file that is both human and machine readable.
+This format represents the first steps toward an open adsorption data format, and the community is encouraged to take up this format.
 
@@
 acknowledges the support of the Alexander von Humboldt foundation and HPC platforms provided by a GENCI grant (A0070807069) and the Center for Information Services and High Performance Computing (ZIH) at TU Dresden.
-  We thank Ren Koh for assistance with the development of the raw2aif file converter and Andrew Tarzia (University College London) for testing the program.
+  We thank Ren Koh for assistance with the development of the raw2aif file converter and Andrew Tarzia (Imperial College London) for testing the program.
 \end{acknowledgement}
